---
title: "IPD MA - Primary and Sensitivity Analysis"
author: "Uyen Doan"
date: "2023-03-23"
output:
  html_document: default
  pdf_document: default
---

# Set up, data-cleaning, & prepare dataset

```{r, message=F}
here::i_am('IPD MA - Primary and Sensitivity Analysis.Rmd')
```

```{r setup, message=F}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999, digits = 5)
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(metafor)
library(nlme)
library(mitml)
library(meta)
library(systemfit)
library(mice)
library(VIM)
library(naniar)
library(standardize)
library(mvmeta)
library(survival)
library(survminer)
library(coxme)
library(gridExtra)
library(psych)
```

```{r loading dataset}
d_other <- read.csv("IPD_additional_all_other_data.csv")
d_ALSPAC <- read.csv("ALSPAC_additional_data.csv")
d_Rice <- read.csv("Rice_data.csv")
d_Hamlat <- read.csv("Hamlat_data.csv")
```

```{r data cleaning}
d_other <- replace(d_other,d_other == -10| d_other==999| d_other==990, NA)
d_other <- d_other %>% filter(!Study == "")
d_ALSPAC <- replace(d_ALSPAC,d_ALSPAC == -10| d_ALSPAC==999| d_ALSPAC==-9999, NA)
```

```{r combine other and alspac dataset}
d <- merge(d_other, d_ALSPAC, by = intersect(names(d_other), names(d_ALSPAC)), all = TRUE)
```

```{r combine Rice and Hamlat datasets with d}
d <- merge(d, d_Rice, by = intersect(names(d), names(d_Rice)), all = TRUE)

d <- merge(d, d_Hamlat, by = intersect(names(d), names(d_Hamlat)), all = TRUE)

d <- d %>% filter(!Study == "" | Study == "Barry")
```

## Imputing relevant variables

```{r}
d <- d %>% mutate(N_total = ifelse(Study %in% c("Nixon_PTSD","Nixon_ASD"), N_pos + N_neg, N_total),
                  N_total = ifelse(Study %in% c("Woody", "Warne", "Hiller"), 10, N_total),
                  N_neg = ifelse(Study %in% c("Woody", "Warne", "Hiller"), 5, N_neg),
                  N_pos = ifelse(Study %in% c("Woody", "Warne", "Hiller"), 5, N_pos))

# add Gender to Hipwell study, only contains female participants
d <- d %>% mutate(Gender = ifelse (Study == "Hipwell", 2, Gender))
```

## Calculating relevant variables

```{r}
d <- d %>% mutate(
  baseMem = ifelse(Study == "Gutenbrunner", Baseline_prop_spec_eo, Baseline_spec/ N_total),
  baseMemNeg = Baseline_spec_neg/N_neg,
  baseMemNeg = ifelse(Study == "Gutenbrunner", Baseline_prop_spec_neg_eo, baseMemNeg),
  baseMemPos = Baseline_spec_pos/N_pos,
  baseMemPos = ifelse(Study == "Gutenbrunner", Baseline_prop_spec_pos_eo, baseMemPos),
  baseDepSx = ifelse(Study %in% c("Askelund", "Gutenbrunner", "Hamlat", "Hitchcock2", "Hitchcock", "Hiller", "Nixon_ASD", "Nixon_PTSD", "Rice", "Sumner", "Woody"),Baseline_self_dep, NA),
  baseDepSx = ifelse(Study %in% c("Hipwell", "McCrory", "Warne"), Baseline_obs_dep_con, baseDepSx),
  depSx6m = ifelse(Study %in% c("Nixon_ASD", "Nixon_PTSD"), Followup_self_dep_2m, NA),
  depSx6m = ifelse(Study == "Askelund", Followup_self_dep_4m, depSx6m),
  depSx6m = ifelse(Study == "Hitchcock", Followup_self_dep_5m, depSx6m),
  depSx6m = ifelse(Study %in% c("Hamlat", "Hiller", "Woody"), Followup_self_dep_6m, depSx6m),
  depSx12m = ifelse(Study %in% c("Askelund", "Gutenbrunner", "Hamlat", "Woody", "Rice"), Followup_self_dep_12m, NA),
  depSx12m = ifelse(Study == "Hitchcock2", Followup_self_dep_8m, depSx12m),
  depSx12m = ifelse(Study %in% c("Hipwell"), Followup_obs_dep_con_12m, depSx12m),
  depSx18m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_dep_18m, NA),
  depSx24m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_dep_24m, NA),
  depSx24m = ifelse(Study == "Gutenbrunner", Followup_self_dep_23m, depSx24m),
  depSx48m = ifelse(Study %in% c("Hamlat","Warne"), Followup_self_dep_48m, NA),
  depSx48m = ifelse(Study == "McCrory", Followup_obs_dep_con_27m, depSx48m),
  baseAnxSx = ifelse(Study %in% c("Gutenbrunner","Hamlat", "Hitchcock2", "Woody"), Baseline_self_anx, NA),
  baseAnxSx = ifelse(Study == "McCrory", Baseline_obs_anx_con, baseAnxSx),
  anxSx6m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_6m, NA),
  anxSx12m = ifelse(Study %in% c("Gutenbrunner", "Hamlat", "Woody"), Followup_self_anx_12m, NA),
  anxSx12m = ifelse(Study == "Hitchcock2", Followup_self_anx_8m, anxSx12m),
  anxSx18m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_18m, NA),
  anxSx24m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_24m, NA),
  anxSx24m = ifelse(Study == "Gutenbrunner", Followup_self_anx_23m, anxSx24m),
  anxSx27m = ifelse(Study == "McCrory", Followup_obs_anx_con_27m, NA),
  basePTSDsx = ifelse(Study %in% c("Hitchcock","Nixon_ASD"), Baseline_int_PTSD_con, NA), 
  basePTSDsx = ifelse(Study %in% c("Hitchcock2","Nixon_PTSD"),Baseline_self_PTSD, basePTSDsx), 
  PTSDsx2m = ifelse(Study %in% c("Hitchcock","Nixon_ASD"), Followup_int_PTSD_con_2m, NA), 
  PTSDsx2m = ifelse(Study == "Nixon_PTSD", Followup_self_PTSD_2m, PTSDsx2m),
  PTSDsx5m = ifelse(Study == "Hitchcock", Followup_int_PTSD_con_5m, NA),
  PTSDsx8m = ifelse(Study == "Hitchcock2", Followup_self_PTSD_8m, NA)
  )

#filter two abnormal data points where proportion of specific memory is >1 and participants without memory data
d <- d[!((d$baseMem > 1.0 | d$baseMemNeg > 1.0) & !(is.na(d$baseMem) | is.na(d$baseMemNeg))),]
d <- d%>% filter(!is.na(baseMem))
```

## z-score transformation

```{r standardisation}
dz <- d %>% group_by(Study)%>%
  mutate(across(starts_with(c("Followup_self", "Followup_obs", "Followup_int_PTSD_con")), scale),
         Baseline_self_dep = scale(Baseline_self_dep),
         Baseline_obs_dep_con = scale(Baseline_obs_dep_con),
         Baseline_self_anx = scale(Baseline_self_anx),
         Baseline_int_PTSD_con = scale(Baseline_int_PTSD_con)) %>%
  ungroup()
```

## Harmonise outcomes between studies

```{r}
dz <- dz %>% 
  mutate(baseDepSx = ifelse(Study %in% c("Askelund", "Gutenbrunner", "Hamlat", "Hitchcock2", "Hitchcock", "Hiller", "Nixon_ASD", "Nixon_PTSD", "Rice", "Sumner", "Woody"),Baseline_self_dep, NA),
         baseDepSx = ifelse(Study %in% c("Hipwell", "McCrory", "Warne"), Baseline_obs_dep_con, baseDepSx),
         depSx6m = ifelse(Study %in% c("Nixon_ASD", "Nixon_PTSD"), Followup_self_dep_2m, NA),
         depSx6m = ifelse(Study == "Askelund", Followup_self_dep_4m, depSx6m),
         depSx6m = ifelse(Study == "Hitchcock", Followup_self_dep_5m, depSx6m),
         depSx6m = ifelse(Study %in% c("Hamlat", "Hiller", "Woody"), Followup_self_dep_6m, depSx6m),
         depSx12m = ifelse(Study %in% c("Askelund", "Gutenbrunner", "Hamlat", "Woody", "Rice"), Followup_self_dep_12m, NA),
         depSx12m = ifelse(Study == "Hitchcock2", Followup_self_dep_8m, depSx12m),
         depSx12m = ifelse(Study %in% c("Hipwell"), Followup_obs_dep_con_12m, depSx12m),
         depSx18m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_dep_18m, NA),
         depSx24m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_dep_24m, NA),
         depSx24m = ifelse(Study == "Gutenbrunner", Followup_self_dep_23m, depSx24m),
         depSx48m = ifelse(Study %in% c("Hamlat","Warne"), Followup_self_dep_48m, NA),
         depSx48m = ifelse(Study == "McCrory", Followup_obs_dep_con_27m, depSx48m),
         depSx72m = ifelse(Study %in% c("Hamlat","Warne"), Followup_self_dep_72m, NA),
         depSx108m = ifelse(Study == "Hamlat", Followup_self_dep_102m, NA),
         depSx108m = ifelse(Study == "Warne", Followup_self_dep_108m, depSx108m),
         baseAnxSx = ifelse(Study %in% c("Gutenbrunner","Hamlat", "Hitchcock2", "Woody"), Baseline_self_anx, NA),
         baseAnxSx = ifelse(Study == "McCrory", Baseline_obs_anx_con, baseAnxSx),
         anxSx6m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_6m, NA),
         anxSx12m = ifelse(Study %in% c("Gutenbrunner", "Hamlat", "Woody"), Followup_self_anx_12m, NA),
         anxSx12m = ifelse(Study == "Hitchcock2", Followup_self_anx_8m, anxSx12m),
         anxSx18m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_18m, NA),
         anxSx24m = ifelse(Study %in% c("Hamlat", "Woody"), Followup_self_anx_24m, NA),
         anxSx24m = ifelse(Study == "Gutenbrunner", Followup_self_anx_23m, anxSx24m),
         anxSx27m = ifelse(Study == "McCrory", Followup_obs_anx_con_27m, NA),
         basePTSDsx = ifelse(Study %in% c("Hitchcock","Nixon_ASD"), Baseline_int_PTSD_con, NA),
         basePTSDsx = ifelse(Study %in% c("Hitchcock2","Nixon_PTSD"),Baseline_self_PTSD, basePTSDsx),
         PTSDsx2m = ifelse(Study %in% c("Hitchcock","Nixon_ASD"), Followup_int_PTSD_con_2m, NA),
         PTSDsx2m = ifelse(Study == "Nixon_PTSD", Followup_self_PTSD_2m, PTSDsx2m),
         PTSDsx5m = ifelse(Study == "Hitchcock", Followup_int_PTSD_con_5m, NA),
         PTSDsx8m = ifelse(Study == "Hitchcock2", Followup_self_PTSD_8m, NA),
         basePsySx = ifelse(Study == "Warne", Baseline_self_psychosis, NA),
         psySx48m = ifelse(Study == "Warne", Followup_self_psychosis_48m, NA),
         depSx = ifelse(Study %in% c("Hitchcock", "Nixon_ASD", "Nixon_PTSD"), Followup_self_dep_2m, NA),
         depSx = ifelse(Study == "Askelund", Followup_self_dep_4m, depSx),
         depSx = ifelse(Study %in% c("Hamlat", "Hiller", "Woody"), Followup_self_dep_6m, depSx),
         depSx = ifelse(Study == "Hitchcock2", Followup_self_dep_8m, depSx),
         depSx = ifelse(Study %in% c("Gutenbrunner", "Rice"), Followup_self_dep_12m, depSx),
         depSx = ifelse(Study == "Hipwell", Followup_obs_dep_con_12m, depSx),
         depSx = ifelse(Study == "McCrory", Followup_obs_dep_con_27m, depSx),
         depSx = ifelse(Study == "Warne", Followup_self_dep_48m, depSx),
         timeDep = ifelse(Study %in% c("Hitchcock", "Nixon_ASD", "Nixon_PTSD"), 2, NA),
         timeDep = ifelse(Study == "Askelund", 4, timeDep),
         timeDep = ifelse(Study %in% c("Hamlat", "Hiller", "Woody"), 6, timeDep),
         timeDep = ifelse(Study == "Hitchcock2", 8, timeDep),
         timeDep = ifelse(Study %in% c("Gutenbrunner", "Hipwell", "Rice"), 12, timeDep),
         timeDep = ifelse(Study == "Warne", 48, timeDep),
         timeDep = ifelse(Study == "McCrory", 27, timeDep))

dz$Sex <- as.numeric(dz$Gender)
```

### Check range, mean, SD of variables against possible range of scales and z-scores

```{r summary stats for d, message=F,warning=F}
d_sum <- d %>% group_by(Study) %>%
  summarise(
    maxMem = max(Baseline_spec, na.rm = T),
    rangeRum = range(Baseline_rum, na.rm = T),
    nameRum = Rum[1],
    rangeSelfDepSx = range(Baseline_self_dep, na.rm = T),
    nameSelfDepSx = Self_dep[1],
    rangeObsDepSx = range(Baseline_obs_dep_con, na.rm = T),
    nameObsDepSx = Obs_dep_con[1],
    rangeSelfAnxSx = range(Baseline_self_anx, na.rm = T),
    nameSelfAnxSx = Self_anx[1],
    rangeObsAnxSx = range(Baseline_obs_anx_con, na.rm = T),
    nameObsAnxSx = Obs_anx_con[1]
  ) %>%
  ungroup()
```

```{r calculate summary statistics for dz}
dz_sum <- dz %>%
  group_by(Study) %>%
  summarise(n=n(), sd_baseDepSx = sd(baseDepSx, na.rm = TRUE),
            mn_baseDepSx = mean(baseDepSx, na.rm = TRUE),
            #range_baseDepSx = range(baseDepSx, na.rm = TRUE),
            sd_baseMem = sd(baseMem, na.rm = TRUE),
            mn_baseMem = mean(baseMem, na.rm = TRUE),
            #range_baseMem = range(baseMem, na.rm = TRUE),
            sd_sxDep6m = sd(depSx6m, na.rm = TRUE),
            mn_sxDep6m = mean(depSx6m, na.rm = TRUE),
            #range_sxDep6m = range(depSx6m, na.rm = TRUE),
            sd_sxDep12m = sd(depSx12m, na.rm = TRUE),
            mn_sxDep12m = mean(depSx12m, na.rm = TRUE),
            #range_sxDep12m = range(depSx12m, na.rm = TRUE),
            sd_sxDep24m = sd(depSx24m, na.rm = TRUE),
            mn_sxDep24m = mean(depSx24m, na.rm = TRUE),
            #range_sxDep24m = range(depSx24m, na.rm = TRUE),
            sd_sxDep48m = sd(depSx48m, na.rm = TRUE),
            mn_sxDep48m = mean(depSx48m, na.rm = TRUE),
            #range_sxDep48m = range(depSx48m, na.rm = TRUE),
            sd_sxDepSx = sd(depSx, na.rm = TRUE),
            mn_sxDepSx = mean(depSx, na.rm = TRUE),
            #range_sxDepSx = range(depSx, na.rm = TRUE),
            sd_baseAnxSx = sd(Baseline_self_anx, na.rm = TRUE),
            mn_baseAnxSx = mean(Baseline_self_anx, na.rm = TRUE),
            #range_baseAnxSx = range(Baseline_self_anx, na.rm = TRUE),
            sd_sxAnx6m = sd(anxSx6m, na.rm = TRUE),
            mn_sxAnx6m = mean(anxSx6m, na.rm = TRUE),
            #range_anx_6m = range(anxSx6m, na.rm = TRUE),
            sd_sxAnx12m = sd(anxSx12m, na.rm = TRUE),
            mn_sxAnx12m = mean(anxSx12m, na.rm = TRUE),
            #range_anx_12m = range(anxSx12m, na.rm = TRUE),
            sd_basePTSDsx = sd(Baseline_int_PTSD_con, na.rm = TRUE),
            mn_basePTSDsx = mean(Baseline_int_PTSD_con, na.rm = TRUE),
            #range_basePTSDsx = range(Baseline_int_PTSD_con, na.rm = TRUE),
            sd_PTSDsx2m = sd(PTSDsx2m, na.rm = TRUE),
            mn_PTSDsx2m = mean(PTSDsx2m, na.rm = TRUE),
            #range_PTSDsx2m = range(PTSDsx2m, na.rm = TRUE),
            sd_PTSDsx5m = sd(PTSDsx5m, na.rm = TRUE),
            mn_PTSDsx5m = mean(PTSDsx5m, na.rm = TRUE),
            #range_PTSDsx5m = range(PTSDsx5m, na.rm = TRUE),
            sd_PTSDsx8m = sd(PTSDsx8m, na.rm = TRUE),
            mn_PTSDsx8m = mean(PTSDsx8m, na.rm = TRUE)) %>%
            #range_PTSDsx8m = range(PTSDsx8m, na.rm = TRUE),) %>%
  ungroup()
```

```{r compile available data}
## Create a table to examine available data by study

study_cols <- list()
for (study_name in unique(d$Study)) {
  study_data <- dz[dz$Study == study_name, ]
  study_cols[[study_name]] <- names(study_data)[apply(study_data, 2, function(x) !all(is.na(x)))]
}
max_length <- max(lengths(study_cols))
var <- lapply(study_cols, function(x) {
  if (length(x) < max_length) {
    x <- c(x, rep(NA, max_length - length(x)))
  }
  return(x[1:max_length])
})
var_df <- dplyr::bind_cols(var)
df_long <- var_df %>% gather(column, value, Askelund:Woody)
df_grouped <- df_long %>% group_by(value)
var_by_study <- df_grouped %>% 
  mutate(column_list = paste(unique(column), collapse = ", "))%>%
  na.omit()
var_by_study$column <- NULL
var_by_study <- distinct(var_by_study)
```

## Missing data examination

```{r}
#using depression sx as main outcome of interest to assess missingness in sx severity outcome
dz <- dz %>% mutate(naDepSx = as.numeric(if_else(is.na(depSx), 0, 1)))

sx.studies <-
  as.character(
    c(
      "Askelund",
      "Gutenbrunner",
      "Hamlat",
      "Hiller",
      "Hipwell",
      "Hitchcock",
      "Hitchcock2",
      "McCrory",
      "Nixon_ASD",
      "Nixon_PTSD",
      "Rice",
      "Warne",
      "Woody"
    )
  )

d.missing.sx <- dz%>% filter(Study %in% sx.studies & (!is.na(Sex))) 
cor.test(d.missing.sx$Age, d.missing.sx$naDepSx)
cor.test(d.missing.sx$Sex, d.missing.sx$naDepSx)
cor.test(d.missing.sx$baseDepSx, d.missing.sx$naDepSx)
cor.test(d.missing.sx$baseMem, d.missing.sx$naDepSx)
```

# Exploratory graph

## Depression

```{r graph, warning=FALSE}
# check distribution of standardised score against unstandardised scores
#standardised dep sx, scatterplot
p.d <- ggplot() +
  geom_point(
    data = dz %>% mutate(timePoint = "06m"),
    mapping = aes(x = baseMem, y = depSx6m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "12m"),
    mapping = aes(x = baseMem, y = depSx12m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "18m"),
    mapping = aes(x = baseMem, y = depSx18m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "24m"),
    mapping = aes(x = baseMem, y = depSx24m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "48m"),
    mapping = aes(x = baseMem, y = depSx48m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.d)

#unstandardised dep sx
p.d.og <- ggplot() +
  geom_point(
    data = d %>% mutate(timePoint = "06m"),
    mapping = aes(x = baseMem, y = depSx6m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "12m"),
    mapping = aes(x = baseMem, y = depSx12m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "18m"),
    mapping = aes(x = baseMem, y = depSx18m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "24m"),
    mapping = aes(x = baseMem, y = depSx24m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "48m"),
    mapping = aes(x = baseMem, y = depSx48m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.d.og)

#boxplot of memory and depression sx
p1 <- ggplot() +
  geom_boxplot(
    data = dz %>% mutate(timePoint = "12m"),
    mapping = aes(x = cut_interval(baseMem, n = 11), y = depSx12m)
  )  + theme_bw() + xlab("baseMem") + theme(axis.text.x = element_text(
    angle = 90,
    hjust = 1,
    vjust = 0.5
  ))

print(p1)

#check correlation
cor.test(dz$baseMem, dz$depSx6m, method = "pearson")
cor.test(dz$baseMem, dz$depSx12m, method = "pearson")
```

## Anxiety sx

```{r graph, warning=FALSE}
p.a <- ggplot() +
  geom_point(
    data = dz %>% mutate(timePoint = "06m"),
    mapping = aes(x = baseMem, y = anxSx6m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "12m"),
    mapping = aes(x = baseMem, y = anxSx12m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "18m"),
    mapping = aes(x = baseMem, y = anxSx18m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "24m"),
    mapping = aes(x = baseMem, y = anxSx24m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.a)

p.a.og <- ggplot() +
  geom_point(
    data = d %>% mutate(timePoint = "06m"),
    mapping = aes(x = baseMem, y = anxSx6m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "12m"),
    mapping = aes(x = baseMem, y = anxSx12m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "18m"),
    mapping = aes(x = baseMem, y = anxSx18m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "24m"),
    mapping = aes(x = baseMem, y = anxSx24m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.a.og)


#check correlation
cor.test(dz$baseMem, dz$anxSx6m, method = "pearson")
cor.test(dz$baseMem, dz$anxSx12m, method = "pearson")
```

## PTSD sx

```{r graph, warning=FALSE}
p.p <- ggplot() +
  geom_point(
    data = dz %>% mutate(timePoint = "2m"),
    mapping = aes(x = baseMem, y = PTSDsx2m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "5m"),
    mapping = aes(x = baseMem, y = PTSDsx5m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = dz %>% mutate(timePoint = "8m"),
    mapping = aes(x = baseMem, y = PTSDsx8m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.p)

p.p.og <- ggplot() +
  geom_point(
    data = d %>% mutate(timePoint = "2m"),
    mapping = aes(x = baseMem, y = PTSDsx2m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "5m"),
    mapping = aes(x = baseMem, y = PTSDsx5m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  geom_point(
    data = d %>% mutate(timePoint = "8m"),
    mapping = aes(x = baseMem, y = PTSDsx8m),
    position = position_jitter(width = 0.03, height = 0.03),
    alpha = 0.25
  ) +
  facet_wrap( ~ timePoint)

print(p.p.og)

#check correlation
cor.test(dz$baseMem, dz$PTSDsx2m, method = "pearson")
cor.test(dz$baseMem, dz$PTSDsx8m, method = "pearson")
```

# Data-analysis

## Primary analysis (symptom severity outcomes)

### Stage one

Analysing all primary symptom outcomes per study

```{r function}
single_ipd = function(df,
                      formula = "depSx12m ~ baseMem + baseDepSx",
                      predictor = 'baseMem') {
  lm = glm(as.formula(formula),
           data = df,
           family = gaussian(link = 'identity'))
  results = list(coef = coef(lm)[predictor],
                 SE = summary(lm)$coef[predictor, 'Std. Error'])
  return(results)
}
```

```{r Askelund}
#depression sx 6m
Ask.d6 <-
  single_ipd(dz %>% filter(Study == "Askelund"), formula = "depSx6m ~baseMem + baseDepSx")
#depression sx 12m
Ask.d12 <- single_ipd(dz %>% filter(Study == "Askelund"))

##positive memory specificity
#depression sx 6m
Ask.d6.pos <-
  single_ipd(dz %>% filter(Study == "Askelund"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")
#depression sx 12m
Ask.d12.pos <-
  single_ipd(dz %>% filter(Study == "Askelund"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
#depression sx 6m
Ask.d6.neg <-
  single_ipd(dz %>% filter(Study == "Askelund"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
#depression sx 12m
Ask.d12.neg <-
  single_ipd(dz %>% filter(Study == "Askelund"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Gutenbrunner}
#depression sx 12m
Gut.d12 <- single_ipd(dz %>% filter(Study == "Gutenbrunner"))
#depression sx 24m
Gut.d24 <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"), formula = "depSx24m ~baseMem + baseDepSx")

#anxiety sx 12m
Gut.a12 <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"), formula = "anxSx12m ~baseMem + baseAnxSx")
#anxiety sx 24m
Gut.a24 <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"), formula = "anxSx24m ~baseMem + baseAnxSx")

##postive memory specificity
#depression sx 12m
Gut.d12.pos <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")
#depression sx 24m
Gut.d24.pos <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"),
             formula = "depSx24m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
#depression sx 12m
Gut.d12.neg <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
#depression sx 24m
Gut.d24.neg <-
  single_ipd(dz %>% filter(Study == "Gutenbrunner"),
             formula = "depSx24m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Hamlat}
#depression sx 6m
Ham.d6 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "depSx6m ~ baseMem + baseDepSx")
#depression sx 12m
Ham.d12 <- single_ipd(dz %>% filter(Study == "Hamlat"))
#depression sx 18m
Ham.d18 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "depSx18m ~baseMem + baseDepSx")
#depression sx 24m
Ham.d24 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "depSx24m ~baseMem + baseDepSx")
#depression sx 48m
Ham.d48 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "depSx48m ~baseMem + baseDepSx")

#anxiety sx 6m
Ham.a6 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "anxSx6m ~baseMem + baseAnxSx")
#anxiety sx 12m
Ham.a12 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "anxSx12m ~baseMem + baseAnxSx")
#anxiety sx 18m
Ham.a18 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "anxSx18m ~baseMem + baseAnxSx")
#anxiety sx 24m
Ham.a24 <-
  single_ipd(dz %>% filter(Study == "Hamlat"), formula = "anxSx24m ~baseMem + baseAnxSx")
```

```{r Hiller}
#depression sx 6m
Hil.d6 <-
  single_ipd(dz %>% filter(Study == "Hiller"), formula = "depSx6m ~ baseMem + baseDepSx")

##positive memory specificity
Hil.d6.pos <-
  single_ipd(dz %>% filter(Study == "Hiller"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Hil.d6.neg <-
  single_ipd(dz %>% filter(Study == "Hiller"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Hipwell}
#depression sx 12m
Hip.d12 <- single_ipd(dz %>% filter(Study == "Hipwell"))

##positive memory specificity
Hip.d12.pos <-
  single_ipd(dz %>% filter(Study == "Hipwell"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Hip.d12.neg <-
  single_ipd(dz %>% filter(Study == "Hipwell"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Hitchcock}
#depression sx 6m
Hit.d6 <-
  single_ipd(dz %>% filter(Study == "Hitchcock"), formula = "depSx6m ~ baseMem + baseDepSx")

#PTSD sx 2m
Hit.p2 <-
  single_ipd(dz %>% filter(Study == "Hitchcock"), formula = "PTSDsx2m ~ baseMem + basePTSDsx")

#PTSD sx 5m
Hit.p5 <-
  single_ipd(dz %>% filter(Study == "Hitchcock"), formula = "PTSDsx5m ~ baseMem + basePTSDsx")

##positive memory specificity
Hit.d6.pos <-
  single_ipd(dz %>% filter(Study == "Hitchcock"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Hit.d6.neg <-
  single_ipd(dz %>% filter(Study == "Hitchcock"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Hitchcock 2}
#depression sx 12m
Hit2.d12 <- single_ipd(dz %>% filter(Study == "Hitchcock2"))

#anxiety sx 12m
Hit2.a12 <-
  single_ipd(dz %>% filter(Study == "Hitchcock2"), formula = "anxSx12m ~ baseMem + baseAnxSx")

#PTSD sx 8m
Hit2.p8 <-
  single_ipd(dz %>% filter(Study == "Hitchcock2"), formula = "PTSDsx8m ~ baseMem + basePTSDsx")

##positive memory specificity
Hit2.d12.pos <-
  single_ipd(dz %>% filter(Study == "Hitchcock2"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Hit2.d12.neg <-
  single_ipd(dz %>% filter(Study == "Hitchcock2"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r McCrory}
#depression sx 48m
Mc.d48 <-
  single_ipd(dz %>% filter(Study == "McCrory"), formula = "depSx48m ~ baseMem + baseDepSx")

#anxiety sx 27m
Mc.a27 <-
  single_ipd(dz %>% filter(Study == "McCrory"), formula = "anxSx27m ~ baseMem + baseAnxSx")

##positive memory specificity
Mc.d48.pos <-
  single_ipd(dz %>% filter(Study == "McCrory"),
             formula = "depSx48m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Mc.d48.neg <-
  single_ipd(dz %>% filter(Study == "McCrory"),
             formula = "depSx48m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Nixon ASD}
#depression sx 6m
NixA.d6 <-
  single_ipd(dz %>% filter(Study == "Nixon_ASD"), formula = "depSx6m ~ baseMem + baseDepSx")

#PTSD sx 2m
NixA.p2 <-
  single_ipd(dz %>% filter(Study == "Nixon_ASD"), formula = "PTSDsx2m ~ baseMem + basePTSDsx")

##positive memory specificity
NixA.d6.pos <-
  single_ipd(dz %>% filter(Study == "Nixon_ASD"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
NixA.d6.neg <-
  single_ipd(dz %>% filter(Study == "Nixon_ASD"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Nixon PTSD}
#depression sx 6m
NixP.d6 <-
  single_ipd(dz %>% filter(Study == "Nixon_PTSD"), formula = "depSx6m ~ baseMem + baseDepSx")

#PTSD sx 2m
NixP.p2 <-
  single_ipd(dz %>% filter(Study == "Nixon_PTSD"), formula = "PTSDsx2m ~ baseMem + basePTSDsx")

##positive memory specificity
NixP.d6.pos <-
  single_ipd(dz %>% filter(Study == "Nixon_PTSD"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
NixP.d6.neg <-
  single_ipd(dz %>% filter(Study == "Nixon_PTSD"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Rice}
#depression sx 12m
Rice.d12 <- single_ipd(dz %>% filter(Study == "Rice"))

##positive memory specificity
Rice.d12.pos <-
  single_ipd(dz %>% filter(Study == "Rice"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Rice.d12.neg <-
  single_ipd(dz %>% filter(Study == "Rice"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Warne}
#depression sx 48m
Warn.d48 <-
  single_ipd(dz %>% filter(Study == "Warne"), formula = "depSx48m ~ baseMem + baseDepSx")

##positive memory specificity
Warn.d48.pos <-
  single_ipd(dz %>% filter(Study == "Warne"),
             formula = "depSx48m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Warn.d48.neg <-
  single_ipd(dz %>% filter(Study == "Warne"),
             formula = "depSx48m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

```{r Woody}
#depression sx 6m
Wood.d6 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "depSx6m ~ baseMem + baseDepSx")
#depression sx 12m
Wood.d12 <- single_ipd(dz %>% filter(Study == "Woody"))
#depression sx 18m
Wood.d18 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "depSx18m ~baseMem + baseDepSx")
#depression sx 24m
Wood.d24 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "depSx24m ~baseMem + baseDepSx")

#anxiety sx 6m
Wood.a6 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "anxSx6m ~baseMem + baseAnxSx")
#anxiety sx 12m
Wood.a12 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "anxSx12m ~baseMem + baseAnxSx")
#anxiety sx 18m
Wood.a18 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "anxSx18m ~baseMem + baseAnxSx")
#anxiety sx 24m
Wood.a24 <-
  single_ipd(dz %>% filter(Study == "Woody"), formula = "anxSx24m ~baseMem + baseAnxSx")

##negative memory specificity
Wood.d6.pos <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx6m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

Wood.d12.pos <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx12m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

Wood.d18.pos <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx18m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

Wood.d24.pos <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx24m ~ baseMemPos + baseDepSx",
             predictor = "baseMemPos")

##negative memory specificity
Wood.d6.neg <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx6m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")

Wood.d12.neg <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx12m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")

Wood.d18.neg <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx18m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")

Wood.d24.neg <-
  single_ipd(dz %>% filter(Study == "Woody"),
             formula = "depSx24m ~ baseMemNeg + baseDepSx",
             predictor = "baseMemNeg")
```

### Multivariate for depression at multiple time points

#### Estimate within-study variance - covariance

```{r Askelund, warning=F}
A_dm1 <- depSx6m ~ baseMem + baseDepSx
A_dm2 <- depSx12m ~ baseMem + baseDepSx

A_dm_fitsur <-
  systemfit(
    list(dep6m = A_dm1, dep12m = A_dm2),
    data = subset(dz, Study == "Askelund"),
    method = "SUR"
  )
Ask_dm_V11 <- A_dm_fitsur$coefCov["dep6m_baseMem", "dep6m_baseMem"]
Ask_dm_V12 <- A_dm_fitsur$coefCov["dep6m_baseMem", "dep12m_baseMem"]
Ask_dm_V22 <- A_dm_fitsur$coefCov["dep12m_baseMem", "dep12m_baseMem"]
```

```{r Gutenbrunner}
G_dm2 <- depSx12m ~ baseMem + baseDepSx 
G_dm4 <- depSx24m ~ baseMem + baseDepSx 

G_dm_fitsur <-
  systemfit(
    list(dep12m = G_dm2, dep24m = G_dm4),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )
Gut_dm_V22 <- G_dm_fitsur$coefCov["dep12m_baseMem", "dep12m_baseMem"]
Gut_dm_V24 <- G_dm_fitsur$coefCov["dep12m_baseMem", "dep24m_baseMem"]
Gut_dm_V44 <- G_dm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
```

```{r Hamlat,warning=F}
H_dm1 <- depSx6m ~ baseMem + baseDepSx 
H_dm2 <- depSx12m ~ baseMem + baseDepSx 
H_dm3 <- depSx18m ~ baseMem + baseDepSx 
H_dm4 <- depSx24m ~ baseMem + baseDepSx
H_dm5 <- depSx48m ~ baseMem + baseDepSx 

H_dm_fitsur <-
  systemfit(
    list(
      dep6m = H_dm1,
      dep12m = H_dm2,
      dep18m = H_dm3,
      dep24m = H_dm4,
      dep48m = H_dm5
    ),
    data = subset(dz, Study == "Hamlat"),
    method = "SUR"
  )

Ham_dm_V11 <- H_dm_fitsur$coefCov["dep6m_baseMem", "dep6m_baseMem"]
Ham_dm_V12 <- H_dm_fitsur$coefCov["dep6m_baseMem", "dep12m_baseMem"]
Ham_dm_V13 <- H_dm_fitsur$coefCov["dep6m_baseMem", "dep18m_baseMem"]
Ham_dm_V14 <- H_dm_fitsur$coefCov["dep6m_baseMem", "dep24m_baseMem"]
Ham_dm_V15 <- H_dm_fitsur$coefCov["dep6m_baseMem", "dep48m_baseMem"]
Ham_dm_V22 <- H_dm_fitsur$coefCov["dep12m_baseMem", "dep12m_baseMem"]
Ham_dm_V23 <- H_dm_fitsur$coefCov["dep12m_baseMem", "dep18m_baseMem"]
Ham_dm_V24 <- H_dm_fitsur$coefCov["dep12m_baseMem", "dep24m_baseMem"]
Ham_dm_V25 <- H_dm_fitsur$coefCov["dep12m_baseMem", "dep48m_baseMem"]
Ham_dm_V33 <- H_dm_fitsur$coefCov["dep18m_baseMem", "dep18m_baseMem"]
Ham_dm_V34 <- H_dm_fitsur$coefCov["dep18m_baseMem", "dep24m_baseMem"]
Ham_dm_V35 <- H_dm_fitsur$coefCov["dep18m_baseMem", "dep48m_baseMem"]
Ham_dm_V44 <- H_dm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
Ham_dm_V45 <- H_dm_fitsur$coefCov["dep24m_baseMem", "dep48m_baseMem"]
Ham_dm_V55 <- H_dm_fitsur$coefCov["dep48m_baseMem", "dep48m_baseMem"]
```

```{r Hiller}
Hil_dm_V11 <- Hil.d6$SE**2 #this gives the same variance as variance-covariance estimates output by stats::vcov()
```

```{r Hipwell}
Hip_dm_V22 <- Hip.d12$SE**2
```

```{r Hitchcock}
Hit_dm_V11 <- Hit.d6$SE**2
```

```{r Hitchcock2}
Hit2_dm_V22 <- Hit2.d12$SE**2
```

```{r McCrory}
Mc_dm_V55 <- Mc.d48$SE**2
```

```{r Nixon_ASD & Nixon_PTSD}
NixA_dm_V11 <- NixA.d6$SE**2

NixP_dm_V11 <- NixP.d6$SE**2
```

```{r Rice}
Rice_dm_V22 <- Rice.d12$SE**2
```

```{r Warne}
Warn_dm_V55 <- Warn.d48$SE**2
```

```{r Woody, warning=F}
Wo_dm1 <- depSx6m ~ baseMem + baseDepSx 
Wo_dm2 <- depSx12m ~ baseMem + baseDepSx 
Wo_dm3 <- depSx18m ~ baseMem + baseDepSx 
Wo_dm4 <- depSx24m ~ baseMem + baseDepSx 

Wo_dm_fitsur <-
  systemfit(
    list(
      dep6m = Wo_dm1,
      dep12m = Wo_dm2,
      dep18m = Wo_dm3,
      dep24m = Wo_dm4
    ),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_dm_V11 <- Wo_dm_fitsur$coefCov["dep6m_baseMem", "dep6m_baseMem"]
Wood_dm_V12 <- Wo_dm_fitsur$coefCov["dep6m_baseMem", "dep12m_baseMem"]
Wood_dm_V13 <- Wo_dm_fitsur$coefCov["dep6m_baseMem", "dep18m_baseMem"]
Wood_dm_V14 <- Wo_dm_fitsur$coefCov["dep6m_baseMem", "dep24m_baseMem"]
Wood_dm_V22 <- Wo_dm_fitsur$coefCov["dep12m_baseMem", "dep12m_baseMem"]
Wood_dm_V23 <- Wo_dm_fitsur$coefCov["dep12m_baseMem", "dep18m_baseMem"]
Wood_dm_V24 <- Wo_dm_fitsur$coefCov["dep12m_baseMem", "dep24m_baseMem"]
Wood_dm_V33 <- Wo_dm_fitsur$coefCov["dep18m_baseMem", "dep18m_baseMem"]
Wood_dm_V34 <- Wo_dm_fitsur$coefCov["dep18m_baseMem", "dep24m_baseMem"]
Wood_dm_V44 <- Wo_dm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
```

#### Stage two

To allow for the inclusion of all studies in a multivariate model with all timepoints, data augmentation approach was used for studies that contributed to at least one but not all timepoints (Riley et al., 2021). In this approach, if an outcome is not measured in a study, coefficient estimate and covariance with other timepoint are 0.0000, and variance is 100000. This essentially means that there is no effect or any correlation with other outcomes, while variance of estimate is so large that it forces the multivariate model to ignore these outcomes when estimating the pooled effect for that timepoint.

```{r}
dep_mv_n <- data.frame (
  Study = c("Askelund et al. 2019", "Gutenbrunner et al. 2018", "Hamlat et al. 2015", "Hiller unpub.", "Hipwell et al. 2011", "Hitchcock et al. 2014", "Hitchcock unpub.", "Puetz et al. 2021", "Nixon et al 2013a", "Nixon et al 2013b", "Rawal & Rice 2012", "Warne et al. 2020", "Woody et al. 2022"),
  n = c(930, 269, 397, 28, 236, 74, 195, 41, 65, 67, 259, 5880, 249),
  dep6m = c(Ask.d6$coef, 0.0000, Ham.d6$coef, Hil.d6$coef, 0.0000, Hit.d6$coef, 0.0000, 0.0000, NixA.d6$coef, NixP.d6$coef, 0.0000, 0.0000,  Wood.d6$coef),
  dep12m = c(Ask.d12$coef, Gut.d12$coef, Ham.d12$coef, 0.0000, Hip.d12$coef, 0.0000, Hit2.d12$coef, 0.0000, 0.0000, 0.0000, Rice.d12$coef, 0.0000, Wood.d12$coef),
  dep18m = c(0.0000, 0.0000, Ham.d18$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d18$coef),
  dep24m = c(0.0000, Gut.d24$coef, Ham.d24$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d24$coef),
  dep48m = c(0.0000, 0.0000, Ham.d48$coef, 0.0000, 0.0000, 0.0000, 0.0000, Mc.d48$coef, 0.0000, 0.0000, 0.0000, Warn.d48$coef, 0.0000),
  V11 = c(Ask_dm_V11, 100000, Ham_dm_V11, Hil_dm_V11, 100000, Hit_dm_V11, 100000, 100000, NixA_dm_V11, NixP_dm_V11, 100000, 100000, Wood_dm_V11),
  V12 = c(Ask_dm_V12, 0.0000, Ham_dm_V12, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V12),
  V13 = c(0.0000, 0.0000, Ham_dm_V13, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V13),
  V14 = c(0.0000, 0.0000, Ham_dm_V14, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V14),
  V15 = c(0.0000, 0.0000, Ham_dm_V15, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V22 = c(Ask_dm_V22, Gut_dm_V22, Ham_dm_V22, 100000, Hip_dm_V22, 100000, Hit2_dm_V22, 100000, 100000, 100000, Rice_dm_V22, 100000, Wood_dm_V22),
  V23 = c(0.0000, 0.0000, Ham_dm_V23, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V23),
  V24 = c(0.0000, Gut_dm_V24, Ham_dm_V24, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V24),
  V25 = c(0.0000, 0.0000, Ham_dm_V25, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V33 = c(100000, 100000, Ham_dm_V33, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dm_V33),
  V34 = c(0.0000, 0.0000, Ham_dm_V34, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V34),
  V35 = c(0.0000, 0.0000, Ham_dm_V35, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V44 = c(100000, Gut_dm_V44, Ham_dm_V44, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dm_V44),
  V45 = c(0.0000, 0.0000, Ham_dm_V45, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V55 = c(100000, 100000, Ham_dm_V55, 100000, 100000, 100000, 100000, Mc_dm_V55, 100000, 100000, 100000, Warn_dm_V55, 100000))
```

Check number of outcomes per studies match expectation

```{r}
dep_mv_desc <-
  dep_mv_n %>% pivot_longer(cols = dep6m:dep48m,
                            values_to = "b",
                            names_to = "Outcome") %>% 
  select(c(Study, n, Outcome, b)) %>% filter(!(b == 0))

dep_mv_desc_sum <-
  dep_mv_desc %>% group_by(Outcome) %>% summarise(N = sum(n)) %>% ungroup()
```

#### Fit Multivariate Mixed-effect Model

```{r}
y <- as.matrix(dep_mv_n[3:7])
S <- as.matrix(dep_mv_n[8:22])
model.dep.mv1 <- mvmeta(y, S)
summary(model.dep.mv1)
```

### Multivariate IPD MA anxiety symptoms

#### Estimate within-study variance - covariance

```{r Gutenbrunner}
G_am2 <- anxSx12m ~ baseMem + baseAnxSx 
G_am4 <- anxSx24m ~ baseMem + baseAnxSx 

G_am_fitsur <-
  systemfit(
    list(anx12m = G_am2, anx24m = G_am4),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )
Gut_am_V22 <- G_am_fitsur$coefCov["anx12m_baseMem", "anx12m_baseMem"]
Gut_am_V24 <- G_am_fitsur$coefCov["anx12m_baseMem", "anx24m_baseMem"]
Gut_am_V44 <- G_am_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

```{r Hamlat, warning=F}
H_am1 <- anxSx6m ~ baseMem + baseAnxSx 
H_am2 <- anxSx12m ~ baseMem + baseAnxSx 
H_am3 <- anxSx18m ~ baseMem + baseAnxSx 
H_am4 <- anxSx24m ~ baseMem + baseAnxSx

H_am_fitsur <-
  systemfit(
    list(
      anx6m = H_am1,
      anx12m = H_am2,
      anx18m = H_am3,
      anx24m = H_am4
    ),
    data = subset(dz, Study == "Hamlat"),
    method = "SUR"
  )

Ham_am_V11 <- H_am_fitsur$coefCov["anx6m_baseMem", "anx6m_baseMem"]
Ham_am_V12 <- H_am_fitsur$coefCov["anx6m_baseMem", "anx12m_baseMem"]
Ham_am_V13 <- H_am_fitsur$coefCov["anx6m_baseMem", "anx18m_baseMem"]
Ham_am_V14 <- H_am_fitsur$coefCov["anx6m_baseMem", "anx24m_baseMem"]
Ham_am_V22 <- H_am_fitsur$coefCov["anx12m_baseMem", "anx12m_baseMem"]
Ham_am_V23 <- H_am_fitsur$coefCov["anx12m_baseMem", "anx18m_baseMem"]
Ham_am_V24 <- H_am_fitsur$coefCov["anx12m_baseMem", "anx24m_baseMem"]
Ham_am_V33 <- H_am_fitsur$coefCov["anx18m_baseMem", "anx18m_baseMem"]
Ham_am_V34 <- H_am_fitsur$coefCov["anx18m_baseMem", "anx24m_baseMem"]
Ham_am_V44 <- H_am_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

```{r Hitchcock2}
Hit2_am_V22 <- Hit2.a12$SE**2
```

```{r Woody,warning=F}
Wo_am1 <- anxSx6m ~ baseMem + baseAnxSx 
Wo_am2 <- anxSx12m ~ baseMem + baseAnxSx 
Wo_am3 <- anxSx18m ~ baseMem + baseAnxSx 
Wo_am4 <- anxSx24m ~ baseMem + baseAnxSx 

Wo_am_fitsur <-
  systemfit(
    list(
      anx6m = Wo_am1,
      anx12m = Wo_am2,
      anx18m = Wo_am3,
      anx24m = Wo_am4
    ),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_am_V11 <- Wo_am_fitsur$coefCov["anx6m_baseMem", "anx6m_baseMem"]
Wood_am_V12 <- Wo_am_fitsur$coefCov["anx6m_baseMem", "anx12m_baseMem"]
Wood_am_V13 <- Wo_am_fitsur$coefCov["anx6m_baseMem", "anx18m_baseMem"]
Wood_am_V14 <- Wo_am_fitsur$coefCov["anx6m_baseMem", "anx24m_baseMem"]
Wood_am_V22 <- Wo_am_fitsur$coefCov["anx12m_baseMem", "anx12m_baseMem"]
Wood_am_V23 <- Wo_am_fitsur$coefCov["anx12m_baseMem", "anx18m_baseMem"]
Wood_am_V24 <- Wo_am_fitsur$coefCov["anx12m_baseMem", "anx24m_baseMem"]
Wood_am_V33 <- Wo_am_fitsur$coefCov["anx18m_baseMem", "anx18m_baseMem"]
Wood_am_V34 <- Wo_am_fitsur$coefCov["anx18m_baseMem", "anx24m_baseMem"]
Wood_am_V44 <- Wo_am_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

#### Stage two

```{r}
anx_mv_n <- data.frame (Study = c("Gutenbrunner", "Hamlat", "Hitchcock2", "Woody"),
                        n = c(269, 397, 195, 249),
                        anx6m = c(0.0000, Ham.a6$coef, 0.0000, Wood.a6$coef),
                        anx12m = c(Gut.a12$coef, Ham.a12$coef, Hit2.a12$coef, Wood.a12$coef),
                        anx18m = c(0.0000, Ham.a18$coef, 0.0000, Wood.a18$coef),
                        anx24m = c(Gut.a24$coef, Ham.a24$coef, 0.0000, Wood.a24$coef),
                        V11 = c(100000, Ham_am_V11, 100000, Wood_am_V11),
                        V12 = c(0.0000, Ham_am_V12, 0.0000, Wood_am_V12),
                        V13 = c(0.0000, Ham_am_V13, 0.0000, Wood_am_V13),
                        V14 = c(0.0000, Ham_am_V14, 0.0000, Wood_am_V14),
                        V22 = c(Gut_am_V22, Ham_am_V22, Hit2_am_V22, Wood_am_V22),
                        V23 = c(0.0000, Ham_am_V23, 0.0000, Wood_am_V23),
                        V24 = c(Gut_am_V24, Ham_am_V24, 0.0000, Wood_am_V24),
                        V33 = c(100000, Ham_am_V33, 100000, Wood_am_V33),
                        V34 = c(0.0000, Ham_am_V34, 0.0000, Wood_am_V34),
                        V44 = c(Gut_am_V44, Ham_am_V44, 100000, Wood_am_V44))
                         
```

```{r}
anx_mv_desc <-
  anx_mv_n %>% pivot_longer(cols = anx6m:anx24m,
                            values_to = "b",
                            names_to = "Outcome") %>% 
  select(c(Study, n, Outcome, b)) %>% filter(!(b == 0))

anx_mv_desc_sum <-
  anx_mv_desc %>% group_by(Outcome) %>% summarise(N = sum(n))
```

#### Fit Multivariate Mixed-effect Model

```{r}
y.anx <- as.matrix(anx_mv_n[3:6])
S.anx <- as.matrix(anx_mv_n[7:16])
anx.mv.model <- mvmeta(y.anx, S.anx)
summary(anx.mv.model)
```

### Multivariate PTSD symptoms

#### Estimate within-study variance - covariance

```{r Hitchcock, warning=F}
H_pm1 <- PTSDsx2m ~ baseMem + basePTSDsx 
H_pm2 <- PTSDsx5m ~ baseMem + basePTSDsx 

H_pm_fitsur <-
  systemfit(
    list(ptsd2m = H_pm1, ptsd5m = H_pm2),
    data = subset(dz, Study == "Hitchcock"),
    method = "SUR"
  )

Hit_pm_V11 <- H_pm_fitsur$coefCov["ptsd2m_baseMem", "ptsd2m_baseMem"]
Hit_pm_V12 <- H_pm_fitsur$coefCov["ptsd2m_baseMem", "ptsd5m_baseMem"]
Hit_pm_V22 <- H_pm_fitsur$coefCov["ptsd5m_baseMem", "ptsd5m_baseMem"]
```

```{r Hitchcock 2}
Hit2_pm_V33 <- Hit2.p8$SE**2
```

```{r Nixon}
NixA_pm_V11 <- NixA.p2$SE**2

NixP_pm_V11 <- NixP.p2$SE**2
```

#### Stage two

```{r make dataframe}
ptsd_mv_n <- data.frame (Study = c("Hitchcock", "Hitchcock2", "Nixon_ASD", "Nixon_PTSD"),
                         n = c(74, 195, 65, 67),
                        ptsd2m = c(Hit.p2$coef, 0.0000, NixA.p2$coef, NixP.p2$coef),
                        ptsd5m = c(Hit.p5$coef, 0.0000, 0.0000, 0.0000),
                        ptsd8m = c(0.0000, Hit2.p8$coef, 0.0000, 0.0000),
                        V11 = c(Hit_pm_V11, 100000, NixA_pm_V11, NixP_pm_V11),
                        V12 = c(Hit_pm_V12, 0.0000, 0.0000, 0.0000),
                        V13 = c(0.0000, 0.0000, 0.0000, 0.0000),
                        V22 = c(Hit_pm_V22, 100000, 100000, 100000),
                        V23 = c(0.0000, 0.0000, 0.0000, 0.0000),
                        V33 = c(100000, Hit2_pm_V33, 100000, 100000))
                         
```

```{r}
ptsd_mv_desc <-
  ptsd_mv_n %>% pivot_longer(cols = ptsd2m:ptsd8m,
                             values_to = "b",
                             names_to = "Outcome") %>% select(c(Study, n, Outcome, b)) %>% filter(!(b == 0))

ptsd_mv_desc_sum <-
  ptsd_mv_desc %>% group_by(Outcome) %>% summarise(N = sum(n))
```

#### Fit Multivariate Mixed-effect Model

```{r}
y.ptsd <- as.matrix(ptsd_mv_n[3:5])
S.ptsd <- as.matrix(ptsd_mv_n[6:11])
ptsd.mv.model <- mvmeta(y.ptsd, S.ptsd)
summary(ptsd.mv.model)
```

### Multivariate for depression at multiple time points \~ positive mem spec

#### Estimate variance - covariance for single study

```{r Askelund, warning=F}
A_dmp1 <- depSx6m ~ baseMemPos + baseDepSx 
A_dmp2 <- depSx12m ~ baseMemPos + baseDepSx 

A_dmp_fitsur <-
  systemfit(
    list(dep6m = A_dmp1, dep12m = A_dmp2),
    data = subset(dz, Study == "Askelund"),
    method = "SUR"
  )

Ask_dmp_V11 <- A_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep6m_baseMemPos"]
Ask_dmp_V12 <- A_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep12m_baseMemPos"]
Ask_dmp_V22 <- A_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep12m_baseMemPos"]
```

```{r Gutenbrunner}
G_dmp2 <- depSx12m ~ baseMemPos + baseDepSx 
G_dmp4 <- depSx24m ~ baseMemPos + baseDepSx 

G_dmp_fitsur <-
  systemfit(
    list(dep12m = G_dmp2, dep24m = G_dmp4),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )
Gut_dmp_V22 <- G_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep12m_baseMemPos"]
Gut_dmp_V24 <- G_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep24m_baseMemPos"]
Gut_dmp_V44 <- G_dmp_fitsur$coefCov["dep24m_baseMemPos", "dep24m_baseMemPos"]
```

```{r Hiller}
Hil_dmp_V11 <- Hil.d6.pos$SE**2
```

```{r Hipwell}
Hip_dmp_V22 <- Hip.d12.pos$SE**2
```

```{r Hitchcock}
Hit_dmp_V11 <- Hit.d6.pos$SE**2
```

```{r Hitchcock2}
Hit2_dmp_V22 <- Hit2.d12.pos$SE**2
```

```{r McCrory}
Mc_dmp_V55 <- Mc.d48.pos$SE**2
```

```{r Nixon_ASD & Nixon_PTSD}
NixA_dmp_V11 <- NixA.d6.pos$SE**2

NixP_dmp_V11 <- NixP.d6.pos$SE**2
```

```{r Rice}
Rice_dmp_V22 <- Rice.d12.pos$SE**2
```

```{r Warne}
Warn_dmp_V55 <- Warn.d48.pos$SE**2
```

```{r Woody, warning=F}
Wo_dmp1 <- depSx6m ~ baseMemPos + baseDepSx 
Wo_dmp2 <- depSx12m ~ baseMemPos + baseDepSx 
Wo_dmp3 <- depSx18m ~ baseMemPos + baseDepSx 
Wo_dmp4 <- depSx24m ~ baseMemPos + baseDepSx 

Wo_dmp_fitsur <-
  systemfit(
    list(
      dep6m = Wo_dmp1,
      dep12m = Wo_dmp2,
      dep18m = Wo_dmp3,
      dep24m = Wo_dmp4
    ),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_dmp_V11 <- Wo_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep6m_baseMemPos"]
Wood_dmp_V12 <- Wo_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep12m_baseMemPos"]
Wood_dmp_V13 <- Wo_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep18m_baseMemPos"]
Wood_dmp_V14 <- Wo_dmp_fitsur$coefCov["dep6m_baseMemPos", "dep24m_baseMemPos"]
Wood_dmp_V22 <- Wo_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep12m_baseMemPos"]
Wood_dmp_V23 <- Wo_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep18m_baseMemPos"]
Wood_dmp_V24 <- Wo_dmp_fitsur$coefCov["dep12m_baseMemPos", "dep24m_baseMemPos"]
Wood_dmp_V33 <- Wo_dmp_fitsur$coefCov["dep18m_baseMemPos", "dep18m_baseMemPos"]
Wood_dmp_V34 <- Wo_dmp_fitsur$coefCov["dep18m_baseMemPos", "dep24m_baseMemPos"]
Wood_dmp_V44 <- Wo_dmp_fitsur$coefCov["dep24m_baseMemPos", "dep24m_baseMemPos"]
```

#### Stage two

```{r}
dep_mv_pos <- data.frame (
  Study = c("Askelund", "Gutenbrunner", "Hiller", "Hipwell", "Hitchcock", "Hitchcock2", "McCrory" ,"Nixon_ASD", "Nixon_PTSD", "Rice", "Warne", "Woody"),
  dep6m = c(Ask.d6.pos$coef, 0.0000, Hil.d6.pos$coef, 0.0000, Hit.d6.pos$coef, 0.0000, 0.0000, NixA.d6.pos$coef, NixP.d6.pos$coef, 0.0000, 0.0000,  Wood.d6.pos$coef),
  dep12m = c(Ask.d12.pos$coef, Gut.d12.pos$coef, 0.0000, Hip.d12.pos$coef, 0.0000, Hit2.d12.pos$coef, 0.0000, 0.0000, 0.0000, Rice.d12.pos$coef, 0.0000, Wood.d12.pos$coef),
  dep18m = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d18.pos$coef),
  dep24m = c(0.0000, Gut.d24.pos$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d24.pos$coef),
  dep48m = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Mc.d48.pos$coef, 0.0000, 0.0000, 0.0000, Warn.d48.pos$coef, 0.0000),
  V11 = c(Ask_dmp_V11, 100000, Hil_dmp_V11, 100000, Hit_dmp_V11, 100000, 100000, NixA_dmp_V11, NixP_dmp_V11, 100000, 100000, Wood_dmp_V11),
  V12 = c(Ask_dmp_V12, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V12),
  V13 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V13),
  V14 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V14),
  V15 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V22 = c(Ask_dmp_V22, Gut_dmp_V22, 100000, Hip_dmp_V22, 100000, Hit2_dmp_V22, 100000, 100000, 100000, Rice_dmp_V22, 100000, Wood_dmp_V22),
  V23 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V23),
  V24 = c(0.0000, Gut_dmp_V24, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V24),
  V25 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V33 = c(100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dmp_V33),
  V34 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmp_V34),
  V35 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V44 = c(100000, Gut_dmp_V44, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dmp_V44),
  V45 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V55 = c(100000, 100000, 100000, 100000, 100000, 100000, Mc_dmp_V55, 100000, 100000, 100000, Warn_dmp_V55, 100000))
```

#### Fit Multivariate Mixed-effect Model

```{r}
y.dpos <- as.matrix(dep_mv_pos[2:6])
S.dpos <- as.matrix(dep_mv_pos[7:21])
model.dep.mv.pos <- mvmeta(y.dpos, S.dpos)
summary(model.dep.mv.pos)
```

### Multivariate for depression at multiple time points \~ negative mem spec

#### Estimate variance - covariance for single study

```{r Askelund, warning=F}
A_dmn1 <- depSx6m ~ baseMemNeg + baseDepSx 
A_dmn2 <- depSx12m ~ baseMemNeg + baseDepSx 

A_dmn_fitsur <-
  systemfit(
    list(dep6m = A_dmn1, dep12m = A_dmn2),
    data = subset(dz, Study == "Askelund"),
    method = "SUR"
  )
Ask_dmn_V11 <- A_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep6m_baseMemNeg"]
Ask_dmn_V12 <- A_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep12m_baseMemNeg"]
Ask_dmn_V22 <- A_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep12m_baseMemNeg"]
```

```{r Gutenbrunner}
G_dmn2 <- depSx12m ~ baseMemNeg + baseDepSx 
G_dmn4 <- depSx24m ~ baseMemNeg + baseDepSx 

G_dmn_fitsur <-
  systemfit(
    list(dep12m = G_dmn2, dep24m = G_dmn4),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )

Gut_dmn_V22 <- G_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep12m_baseMemNeg"]
Gut_dmn_V24 <- G_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep24m_baseMemNeg"]
Gut_dmn_V44 <- G_dmn_fitsur$coefCov["dep24m_baseMemNeg", "dep24m_baseMemNeg"]
```

```{r Hiller}
Hil_dmn_V11 <- Hil.d6.neg$SE**2
```

```{r Hipwell}
Hip_dmn_V22 <- Hip.d12.neg$SE**2
```

```{r Hitchcock}
Hit_dmn_V11 <- Hit.d6.neg$SE**2
```

```{r Hitchcock2}
Hit2_dmn_V22 <- Hit2.d12.neg$SE**2
```

```{r McCrory}
Mc_dmn_V55 <- Mc.d48.neg$SE**2
```

```{r Nixon_ASD & Nixon_PTSD}
NixA_dmn_V11 <- NixA.d6.neg$SE**2

NixP_dmn_V11 <- NixP.d6.neg$SE**2
```

```{r Rice}
Rice_dmn_V22 <- Rice.d12.neg$SE**2
```

```{r Warne}
Warn_dmn_V55 <- Warn.d48.neg$SE**2
```

```{r Woody, warning=F}
Wo_dmn1 <- depSx6m ~ baseMemNeg + baseDepSx 
Wo_dmn2 <- depSx12m ~ baseMemNeg + baseDepSx 
Wo_dmn3 <- depSx18m ~ baseMemNeg + baseDepSx 
Wo_dmn4 <- depSx24m ~ baseMemNeg + baseDepSx 

Wo_dmn_fitsur <-
  systemfit(
    list(
      dep6m = Wo_dmn1,
      dep12m = Wo_dmn2,
      dep18m = Wo_dmn3,
      dep24m = Wo_dmn4
    ),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_dmn_V11 <- Wo_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep6m_baseMemNeg"]
Wood_dmn_V12 <- Wo_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep12m_baseMemNeg"]
Wood_dmn_V13 <- Wo_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep18m_baseMemNeg"]
Wood_dmn_V14 <- Wo_dmn_fitsur$coefCov["dep6m_baseMemNeg", "dep24m_baseMemNeg"]
Wood_dmn_V22 <- Wo_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep12m_baseMemNeg"]
Wood_dmn_V23 <- Wo_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep18m_baseMemNeg"]
Wood_dmn_V24 <- Wo_dmn_fitsur$coefCov["dep12m_baseMemNeg", "dep24m_baseMemNeg"]
Wood_dmn_V33 <- Wo_dmn_fitsur$coefCov["dep18m_baseMemNeg", "dep18m_baseMemNeg"]
Wood_dmn_V34 <- Wo_dmn_fitsur$coefCov["dep18m_baseMemNeg", "dep24m_baseMemNeg"]
Wood_dmn_V44 <- Wo_dmn_fitsur$coefCov["dep24m_baseMemNeg", "dep24m_baseMemNeg"]
```

#### Stage two

```{r}
dep_mv_neg <- data.frame (
  Study = c("Askelund", "Gutenbrunner", "Hiller", "Hipwell", "Hitchcock", "Hitchcock2", "McCrory" ,"Nixon_ASD", "Nixon_PTSD", "Rice", "Warne", "Woody"),
  dep6m = c(Ask.d6.neg$coef, 0.0000, Hil.d6.neg$coef, 0.0000, Hit.d6.neg$coef, 0.0000, 0.0000, NixA.d6.neg$coef, NixP.d6.neg$coef, 0.0000, 0.0000,  Wood.d6.neg$coef),
  dep12m = c(Ask.d12.neg$coef, Gut.d12.neg$coef, 0.0000, Hip.d12.neg$coef, 0.0000, Hit2.d12.neg$coef, 0.0000, 0.0000, 0.0000, Rice.d12.neg$coef, 0.0000, Wood.d12.neg$coef),
  dep18m = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d18.neg$coef),
  dep24m = c(0.0000, Gut.d24.neg$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d24.neg$coef),
  dep48m = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Mc.d48.neg$coef, 0.0000, 0.0000, 0.0000, Warn.d48.neg$coef, 0.0000),
  V11 = c(Ask_dmn_V11, 100000, Hil_dmn_V11, 100000, Hit_dmn_V11, 100000, 100000, NixA_dmn_V11, NixP_dmn_V11, 100000, 100000, Wood_dmn_V11),
  V12 = c(Ask_dmn_V12, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V12),
  V13 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V13),
  V14 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V14),
  V15 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V22 = c(Ask_dmn_V22, Gut_dmn_V22, 100000, Hip_dmn_V22, 100000, Hit2_dmn_V22, 100000, 100000, 100000, Rice_dmn_V22, 100000, Wood_dmn_V22),
  V23 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V23),
  V24 = c(0.0000, Gut_dmn_V24, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V24),
  V25 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V33 = c(100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dmn_V33),
  V34 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dmn_V34),
  V35 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V44 = c(100000, Gut_dmn_V44, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dmn_V44),
  V45 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V55 = c(100000, 100000, 100000, 100000, 100000, 100000, Mc_dmn_V55, 100000, 100000, 100000, Warn_dmn_V55, 100000))
```

```{r}
y.dneg <- as.matrix(dep_mv_neg[2:6])
S.dneg <- as.matrix(dep_mv_neg[7:21])
model.dep.mv.neg <- mvmeta(y.dneg, S.dneg)
summary(model.dep.mv.neg)
```

### Multivariate model all symptoms at 18 and 24 months, predicted by mem spec

#### Estimate variance - covariance for single study

```{r Gutenbrunner}
G_sxm_fitsur <-
  systemfit(
    list(dep24m = G_dm4, anx24m = G_am4),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )

Gut_sxm_V33 <- G_sxm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
Gut_sxm_V34 <- G_sxm_fitsur$coefCov["dep24m_baseMem", "anx24m_baseMem"]
Gut_sxm_V44 <- G_sxm_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

```{r Hamlat, warning=F}
H_sxm_fitsur <-
  systemfit(
    list(
      dep18m = H_dm3,
      anx18m = H_am3,
      dep24m = H_dm4,
      anx24m = H_am4
    ),
    data = subset(dz, Study == "Hamlat"),
    method = "SUR"
  )

Ham_sxm_V11 <- H_sxm_fitsur$coefCov["dep18m_baseMem", "dep18m_baseMem"]
Ham_sxm_V12 <- H_sxm_fitsur$coefCov["dep18m_baseMem", "anx18m_baseMem"]
Ham_sxm_V13 <- H_sxm_fitsur$coefCov["dep18m_baseMem", "dep24m_baseMem"]
Ham_sxm_V14 <- H_sxm_fitsur$coefCov["dep18m_baseMem", "anx24m_baseMem"]
Ham_sxm_V22 <- H_sxm_fitsur$coefCov["anx18m_baseMem", "anx18m_baseMem"]
Ham_sxm_V23 <- H_sxm_fitsur$coefCov["anx18m_baseMem", "dep24m_baseMem"]
Ham_sxm_V24 <- H_sxm_fitsur$coefCov["anx18m_baseMem", "anx24m_baseMem"]
Ham_sxm_V33 <- H_sxm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
Ham_sxm_V34 <- H_sxm_fitsur$coefCov["dep24m_baseMem", "anx24m_baseMem"]
Ham_sxm_V44 <- H_sxm_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

```{r Woody, warning=F}
Wo_sxm_fitsur <-
  systemfit(
    list(
      dep18m = Wo_dm3,
      anx18m = Wo_am3,
      dep24m = Wo_dm4,
      anx24m = Wo_am4
    ),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_sxm_V11 <- Wo_sxm_fitsur$coefCov["dep18m_baseMem", "dep18m_baseMem"]
Wood_sxm_V12 <- Wo_sxm_fitsur$coefCov["dep18m_baseMem", "anx18m_baseMem"]
Wood_sxm_V13 <- Wo_sxm_fitsur$coefCov["dep18m_baseMem", "dep24m_baseMem"]
Wood_sxm_V14 <- Wo_sxm_fitsur$coefCov["dep18m_baseMem", "anx24m_baseMem"]
Wood_sxm_V22 <- Wo_sxm_fitsur$coefCov["anx18m_baseMem", "anx18m_baseMem"]
Wood_sxm_V23 <- Wo_sxm_fitsur$coefCov["anx18m_baseMem", "dep24m_baseMem"]
Wood_sxm_V24 <- Wo_sxm_fitsur$coefCov["anx18m_baseMem", "anx24m_baseMem"]
Wood_sxm_V33 <- Wo_sxm_fitsur$coefCov["dep24m_baseMem", "dep24m_baseMem"]
Wood_sxm_V34 <- Wo_sxm_fitsur$coefCov["dep24m_baseMem", "anx24m_baseMem"]
Wood_sxm_V44 <- Wo_sxm_fitsur$coefCov["anx24m_baseMem", "anx24m_baseMem"]
```

#### Stage two

```{r}
sx_mv <- data.frame (Study = c("Gutenbrunner", "Hamlat", "Woody"),
                     dep18m = c(0.0000, Ham.d18$coef, Wood.d18$coef),
                     anx18m = c(0.0000, Ham.a18$coef, Wood.a18$coef),
                     dep24m = c(Gut.d24$coef, Ham.d24$coef, Wood.d24$coef),
                     anx24m = c(Gut.a24$coef, Ham.a24$coef, Wood.a24$coef),
                     V11 = c(100000, Ham_sxm_V11, Wood_sxm_V11),
                     V12 = c(0.0000, Ham_sxm_V12, Wood_sxm_V12),
                     V13 = c(0.0000, Ham_sxm_V13, Wood_sxm_V13),
                     V14 = c(0.0000, Ham_sxm_V14, Wood_sxm_V14),
                     V22 = c(100000, Ham_sxm_V22, Wood_sxm_V22),
                     V23 = c(0.0000, Ham_sxm_V23, Wood_sxm_V23),
                     V24 = c(0.0000, Ham_sxm_V24, Wood_sxm_V24),
                     V33 = c(Gut_sxm_V33, Ham_sxm_V33, Wood_sxm_V33),
                     V34 = c(Gut_sxm_V34, Ham_sxm_V34, Wood_sxm_V34),
                     V44 = c(Gut_sxm_V44, Ham_sxm_V44, Wood_sxm_V44))
```

```{r}
y.sx <- as.matrix(sx_mv[2:5])
S.sx <- as.matrix(sx_mv[6:15])
model.sx.mv1 <- mvmeta(y.sx, S.sx)
summary(model.sx.mv1)
```

### Graph for symptoms

```{r}
forest.models = do.call('c', lapply(list(dep_mv_n, anx_mv_n, ptsd_mv_n), function(data){
  outcome_col_numbers = grep("m$", colnames(data))
  forest.model.list = lapply(outcome_col_numbers, function(col_n){
  # filter
    data$yi = data[,col_n]
    variable_number = match(col_n, outcome_col_numbers)
    data$vi = data[,paste0("V", variable_number,variable_number)]
    forest.model <- rma.uni(yi = yi, vi = vi, slab = Study, data = data %>% filter (yi != 0), method = "REML")
    return(forest.model)
  })
  names(forest.model.list) = colnames(data)[outcome_col_numbers]
  return(forest.model.list)
}))
```

#### Depressive sx all time points

```{r}
forest.plot.d6 <-
  forest(
    forest.models$dep6m,
    header = c("Authors and Year", "b Estimate [95%CI]"),
    at = seq(-4, 4, by = 2)
  )
forest.plot.d12 <-
  forest(forest.models$dep12m, at = seq(-4, 4, by = 2))
forest.plot.d18 <- forest(forest.models$dep18m, alim = c(-4, 4))
forest.plot.d24 <- forest(forest.models$dep24m, alim = c(-4, 4))
forest.plot.d48 <- forest(forest.models$dep48m, alim = c(-4, 4))
```

### Funnel plots

```{r}
funnel.rma(forest.models$dep6m)
funnel.rma(forest.models$dep12m)
```

## Sensitivity analysis (symptom severity outcomes)

### One-stage univariate models (pre-registered models)

```{r}
depSx12.uni  <-  lme(depSx12m ~ baseMem + baseDepSx ,
                   data = dz,
                   random    = ~ 1 + baseMem| Study,
                   na.action = na.omit,
                   control   = lmeControl(opt='optim'))

summary(depSx12.uni)
```

```{r}
anxSx12.uni  <-  lme(anxSx12m ~ baseMem + baseAnxSx ,
                   data = dz,
                   random    = ~ 1 + baseMem| Study,
                   na.action = na.omit,
                   control   = lmeControl(opt='optim'))

summary(anxSx12.uni)
```

```{r}
PTSDsx2.uni <-  lme(PTSDsx2m ~ baseMem + basePTSDsx,
                   data = dz,
                   random    = ~ 1 + baseMem| Study,
                   na.action = na.omit,
                   control   = lmeControl(opt='optim'))

summary(PTSDsx2.uni)
```

### One-stage univariate models (with unstandardised score)

```{r}
summary (
  lme(
    depSx12m ~ baseMem + baseDepSx ,
    data = d,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

```{r}
summary(
  lme(
    anxSx12m ~ baseMem + baseAnxSx ,
    data = d,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

```{r}
summary(
  lme(
    PTSDsx2m ~ baseMem + basePTSDsx,
    data = d,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

### One-stage univariate models (with Age, Sex and IQ where available)

```{r}
summary (
  lme(
    depSx12m ~ baseMem + baseDepSx + Age + Sex + Baseline_IQ,
    data = dz,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

```{r}
summary(
  lme(
    anxSx12m ~ baseMem + baseAnxSx + Age + Sex,
    data = dz,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

```{r}
summary(
  lme(
    PTSDsx2m ~ baseMem + basePTSDsx + Age + Sex,
    data = dz,
    random    = ~ 1 + baseMem | Study,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )
)
```

## Primary analysis (Diagnosis models - survival analysis)

### Presence of any diagnosis

#### Calculate presence of diagnosis and time to first onset variables

```{r, warning=F}
# look for columns that have _dia_ (for diagnosis)
diagnosis.columns = grep("^Base.*_dia$|_dia_", var_by_study$value, value=TRUE)
# check if column starts with Base to set time=0, otherwise extract time in months from end of column name
diagnosis.columns.time = ifelse(grepl("^Base", diagnosis.columns), 0, as.numeric(gsub(".*_dia_", "", gsub("m$", "", diagnosis.columns))))
diagnosis.columns.name = gsub("_dia.*$", "", gsub(".*_int_", "", diagnosis.columns))
dz = as.data.frame(dz)
dz$Diagnosed_disorder = ""
dz$Diagnosis_time = NA
dz$First_Diagnosis = NA
dz$Is_Diagnosed = NA
dz[,sort(unique(diagnosis.columns.name))] = NA
dz[,paste(sort(unique(diagnosis.columns.name)),"_time",sep='')] = NA

for(i in 1:length(diagnosis.columns)){
  column = diagnosis.columns[i]
  time=diagnosis.columns.time[i]
  diagnosis = diagnosis.columns.name[i]
  diagnosis.time = paste(diagnosis, "_time", sep = '')
  diagnosed.rows = which(dz[,column] == 1) 
  undiagnosed.rows = which(dz[,column] == 0)
  still.undiagnosed.rows = intersect(undiagnosed.rows, which(dz[,diagnosis]==0))
  newly.undiagnosed.rows = intersect(undiagnosed.rows, which(is.na(dz[,diagnosis])))
  already.diagnosed.rows = intersect(diagnosed.rows, which(dz[,diagnosis]==1))
  newly.diagnosed.rows = setdiff(diagnosed.rows, which(dz[,diagnosis]==1))
  
  dz[diagnosed.rows,diagnosis] = 1
  dz[undiagnosed.rows,diagnosis] = ifelse(is.na(dz[undiagnosed.rows,diagnosis]), 0,
                                          pmax(dz[undiagnosed.rows,diagnosis],0)) 
  # pmax (parallel maximum) sets to 0 if already 0 and 1 if already diagnosed
  if(length(already.diagnosed.rows)>0){
     dz[already.diagnosed.rows,diagnosis.time] = pmin(dz[already.diagnosed.rows,diagnosis.time], time,na.rm=T)
  }
  if(length(newly.diagnosed.rows)>0){
    dz[newly.diagnosed.rows,diagnosis.time] = time
  }
 
  if(length(still.undiagnosed.rows)>0){
    dz[still.undiagnosed.rows,diagnosis.time] = pmax(dz[still.undiagnosed.rows,diagnosis.time], time,na.rm=T)
  }
  if(length(newly.undiagnosed.rows)>0){
    dz[newly.undiagnosed.rows,diagnosis.time] = time
  }
  
  
}
all.diagnosis.names = sort(unique(diagnosis.columns.name))
all.diagnosis.times = paste(all.diagnosis.names, "_time", sep='')
dz$Diagnosed_disorder = apply(dz[,all.diagnosis.names], 1, function(i){paste(all.diagnosis.names[which(i==1)],collapse=', ')})
dz$First_Diagnosis = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names] == 1)
  if(length(diagnoses)==0){return('')}
  return(paste(all.diagnosis.names[diagnoses][which(dz[i,all.diagnosis.times][diagnoses] == min(dz[i,all.diagnosis.times][diagnoses], na.rm=T))], collapse=', '))
})
dz$Diagnosis_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][diagnoses],na.rm=T))
  }
})
dz$Is_Diagnosed = as.integer(rowSums(dz[,all.diagnosis.names], na.rm = T) > 0)
dz$Is_Diagnosed = ifelse(is.na(dz$Diagnosis_time), NA, dz$Is_Diagnosed)

#manually check
#dia='MDD';View(dz[,c(paste0(dia,"_time"), dia, diagnosis.columns[diagnosis.columns.name==dia])])
```

#### Exploratory graphs

```{r}
ggplot(dz %>% 
         filter(!is.na(Diagnosis_time)), aes(x = factor(Is_Diagnosed), 
                                             y = baseMem)) + geom_boxplot() + 
  facet_wrap(~ Diagnosis_time) + 
  theme_bw() +
  xlab("Any disorder diagnosis") + 
  ylab("Baseline Memory Specificity") 
```

#### Assess missingness

```{r}
#using all dx as main outcome of interest to assessed missingness
dz <- dz %>% 
  mutate(naDiagnosis = as.numeric(if_else(is.na(Is_Diagnosed), 0, 1)))

diagnosis.studies <-
  as.character(c("Askelund", "Hamlat", "Hipwell", "Rice", "Sumner"))

d.missing.diagnosis <- dz %>% filter(Study %in% diagnosis.studies)
cor.test(d.missing.diagnosis$Age, d.missing.diagnosis$naDiagnosis)
cor.test(d.missing.diagnosis$Sex, d.missing.diagnosis$naDiagnosis)
cor.test(d.missing.diagnosis$baseMem, d.missing.diagnosis$naDiagnosis)
```

#### Fit mixed-effect Cox survival model

```{r survival analysis model}
dz$Study.f <- as.factor(dz$Study)
dz$Study.n <- as.numeric(dz$Study.f)

#Categorise baseline memory for plotting survival curve
dz$memCat <-
  cut(
    dz$baseMem,
    breaks = 3,
    labels = c(
      "Low memory specificity",
      "Mid memory specificity",
      "High memory specificity"
    )
  )

dia.object <- Surv(dz$Diagnosis_time, dz$Is_Diagnosed)

dia.cox.rand.clustered <-
  coxme(
    dia.object ~ baseMem + (baseMem |
                              Study.n) + Study,
    data = dz,
    ties = c("breslow")
  )
dia.cox.rand.clustered
#95%CI for HR
exp(confint(dia.cox.rand.clustered))

#HR for 10% reduction in mem spec
any.dia.HR.10 <- exp(dia.cox.rand.clustered$coefficients[["baseMem"]]* (-0.1))
any.dia.HR.10
any.dia.timeRatio.10 <- 1/any.dia.HR.10
any.dia.timeRatio.10
```

```{r}
ggsurvplot(
  surv_fit(dia.object ~  memCat, data = dz),
  palette = "grey",
  xlab = "Time to First Diagnosis (months)",
  ylab = "Probability of Absent Diagnosis",
  legend.title = "Memory category",
  legend.labs = c(
    "Low Memory Specificity",
    "Mid Memory Specificity",
    "High Memory Specificity"
  )
)
```

#### Exploring cue valence

```{r}
dia.pos.cox.rand.clustered <- coxme(dia.object ~ baseMemPos + (baseMemPos | Study.n) + Study, data = dz, ties = c("breslow"))
dia.pos.cox.rand.clustered

dia.neg.cox.rand.clustered <- coxme(dia.object ~ baseMemNeg + (baseMemNeg | Study.n) + Study, data = dz, ties = c("breslow"))
dia.neg.cox.rand.clustered
```

#### Additional analysis with only diagnosis-free participants at baseline

```{r}
dz.dia.free <- dz %>% filter(!(Is_Diagnosed == 1 & Diagnosis_time == 0))
dia.free.surv.object <- Surv(dz.dia.free$Diagnosis_time, dz.dia.free$Is_Diagnosed)

dia.free.cox.rand.clustered <- coxme(
  dia.free.surv.object ~ baseMem + (baseMem |
                                      Study) + Study,
  data = dz.dia.free,
  ties = c("breslow")
)
dia.free.cox.rand.clustered
exp(confint(dia.free.cox.rand.clustered))

#95%CI for HR
exp(confint(dia.free.cox.rand.clustered))

#HR for 10% reduction in mem spec
any.dia.HR.10 <- exp(dia.free.cox.rand.clustered$coefficients[["baseMem"]]* (-0.1))
any.dia.HR.10
any.dia.timeRatio.10 <- 1/any.dia.HR.10
any.dia.timeRatio.10
```

```{r}
ggsurvplot(
  surv_fit(dia.free.surv.object ~  memCat, data = dz.dia.free),
  palette = "grey",
  xlab = "Time to First Diagnosis (months)",
  ylab = "Probability of Absent Diagnosis",
  legend.title = "Memory Category",
  legend.labs = c(
    "Low Memory Specificity",
    "Mid Memory Specificity",
    "High Memory Specificity"
  )
)
```

### Presence of depressive disorders

```{r calculate variables}
depressive.disorder.group = c("CMDD", "MDD", "dep", "dys", "minor_dep")
in.disorder.group = all.diagnosis.names %in% depressive.disorder.group

dz$Depressive_disorders_diagnosed = as.integer(rowSums(dz[,depressive.disorder.group], na.rm=T) > 0)

dz$Depressive_disorders_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names][in.disorder.group] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times][in.disorder.group]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times][in.disorder.group], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][in.disorder.group][diagnoses],na.rm=T))
  }
})

#View(dz[,c("Depressive_disorders_diagnosed", "Depressive_disorders_time", depressive.disorder.group, paste0(depressive.disorder.group,"_time"))])
```

#### Exploratory graphs

```{r}
ggplot(dz %>% filter(!is.na(Depressive_disorders_time)), aes(x = factor(Depressive_disorders_diagnosed), y =
                                                               baseMem)) + geom_boxplot() + facet_wrap( ~ Depressive_disorders_time) + theme_bw() +
  xlab("Any depressive disorder diagnosis") + ylab("Baseline Memory Specificity") 
```

#### Fit mixed-effect Cox model

```{r survival analysis models}
dep_dia_object <-
  Surv(dz$Depressive_disorders_time,
       dz$Depressive_disorders_diagnosed)

dep.dia.cox.rand.clustered <- coxme(dep_dia_object ~ baseMem + (baseMem| Study.n) + Study, data = dz, ties = c("breslow"))
dep.dia.cox.rand.clustered
#95%CI for HR
exp(confint(dep.dia.cox.rand.clustered))

#HR for 10% reduction in mem spec
dep.dia.HR.10 <- exp(dep.dia.cox.rand.clustered$coefficients[["baseMem"]]* (-0.1))
dep.dia.HR.10
dep.dia.timeRatio.10 <- 1/dep.dia.HR.10
dep.dia.timeRatio.10
```

```{r plot}
dep.dia.plot <- surv_fit(dep_dia_object ~ memCat, data = dz)
ggsurvplot(
  dep.dia.plot,
  palette = "grey",
  pval = F,
  xlab = "Time to First Depression Diagnosis (months)",
  ylab = "Probability of Absent Depressive Diagnosis",
  legend.title = "Memory Category",
  legend.labs = c(
    "Low Memory Specificity",
    "Mid Memory Specificity",
    "High Memory Specificity"
  )
)
```

```{r}
dz.dep.dia.free <- dz %>% filter(!(Depressive_disorders_diagnosed == 1 & Depressive_disorders_time == 0))
dep.dia.free.surv.object <- Surv(
  dz.dep.dia.free$Depressive_disorders_time,
  dz.dep.dia.free$Depressive_disorders_diagnosed
)

dep.dia.free.cox.rand.clustered <- coxme(
  dep.dia.free.surv.object ~ baseMem + (baseMem |
                                      Study) + Study + Baseline_IQ + Age + Sex,
  data = dz.dep.dia.free,
  ties = c("breslow")
)
dep.dia.free.cox.rand.clustered
exp(confint(dep.dia.free.cox.rand.clustered))

```

### Presence of eating disorders

```{r calculate variables}
eating.disorder.group = c("anorexia", "binge", "bulimia", "eating", "ednos")
in.eating.disorder.group = all.diagnosis.names %in% eating.disorder.group

dz$Eating_disorders_diagnosed = as.integer(rowSums(dz[,eating.disorder.group], na.rm=T) > 0)

dz$Eating_disorders_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names][in.eating.disorder.group] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times][in.eating.disorder.group]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times][in.eating.disorder.group], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][in.eating.disorder.group][diagnoses],na.rm=T))
  }
})
```

```{r survival analysis models}
eat_dia_object <- Surv(dz$Eating_disorders_time, dz$Eating_disorders_diagnosed)

eat.dia.cox.rand.clustered <- coxme(eat_dia_object ~ baseMem + (baseMem| Study.n) + Study, data = dz, ties = c("breslow"))
eat.dia.cox.rand.clustered #model converged too early, likely due to small number of cases and large number of parameters to estimates, thus, we used a simpler model without random effects of baseline memory by Study.

eat.dia.cox.strata <- coxph(eat_dia_object ~ strata(Study.f) + baseMem, data = dz, ties = c("breslow"))
eat.dia.cox.strata
#95%CI for HR
exp(confint(eat.dia.cox.strata))

#HR for 10% reduction in mem spec
eat.dia.HR.10 <- exp(eat.dia.cox.strata$coefficients[["baseMem"]]* (-0.1))
eat.dia.HR.10
eat.dia.timeRatio.10 <- 1/eat.dia.HR.10
eat.dia.timeRatio.10
```

### Presence of anxiety disorders

```{r calculate variables}
anx.disorder.group = c("anx", "GAD", "panic", "social_phobia")
in.anx.disorder.group = all.diagnosis.names %in% anx.disorder.group

dz$Anxiety_disorders_diagnosed = as.integer(rowSums(dz[,anx.disorder.group], na.rm=T) > 0)

dz$Anxiety_disorders_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names][in.anx.disorder.group] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times][in.anx.disorder.group]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times][in.anx.disorder.group], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][in.anx.disorder.group][diagnoses],na.rm=T))
  }
})
```

```{r survival analysis models}
anx_dia_object <- Surv(dz$Anxiety_disorders_time, dz$Anxiety_disorders_diagnosed)

anx.dia.cox.rand.clustered <- coxme(anx_dia_object ~ baseMem + (baseMem| Study.n) + Study, data = dz, ties = c("breslow"))
anx.dia.cox.rand.clustered
#95%CI for HR
exp(confint(anx.dia.cox.rand.clustered))
```

### Presence of posttraumatric stress disorder diagnosis

```{r calculate variables}
stress.disorder.group = c("PTSD", "ASD")
in.stress.disorder.group = all.diagnosis.names %in% stress.disorder.group

dz$Stress_disorders_diagnosed = as.integer(rowSums(dz[,stress.disorder.group], na.rm=T) > 0)

dz$Stress_disorders_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names][in.stress.disorder.group] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times][in.stress.disorder.group]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times][in.stress.disorder.group], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][in.stress.disorder.group][diagnoses],na.rm=T))
  }
})
```

```{r survival analysis models}
Stress_dia_object <- Surv(dz$Stress_disorders_time, dz$Stress_disorders_diagnosed)

Stress.dia.cox.rand.clustered <- coxme(Stress_dia_object ~ baseMem + (baseMem| Study.n) + Study, data = dz, ties = c("breslow"))
Stress.dia.cox.rand.clustered
#95%CI for HR
exp(confint(Stress.dia.cox.rand.clustered))
```

### Presence of bipolar diagnosis

```{r calculate variables}
bipolar.disorder.group = c("bip1", "bip2")
in.bipolar.disorder.group = all.diagnosis.names %in% bipolar.disorder.group

dz$Bipolar_disorders_diagnosed = as.integer(rowSums(dz[,bipolar.disorder.group], na.rm=T) > 0)

dz$Bipolar_disorders_time = sapply(1:nrow(dz), function(i){
  diagnoses = which(dz[i,all.diagnosis.names][in.bipolar.disorder.group] == 1)
  if(sum(!is.na(dz[i,all.diagnosis.times][in.bipolar.disorder.group]))==0){return(NA)}
  if(length(diagnoses)==0){
    return(max(dz[i,all.diagnosis.times][in.bipolar.disorder.group], na.rm=T))
  } else {
    return(min(dz[i,all.diagnosis.times][in.bipolar.disorder.group][diagnoses],na.rm=T))
  }
})
```

```{r survival analysis models}
Bipolar_dia_object <- Surv(dz$Bipolar_disorders_time, dz$Bipolar_disorders_diagnosed)

Bipolar.dia.cox.rand.clustered <- coxme(Bipolar_dia_object ~ baseMem + (baseMem| Study.f) + Study, data = dz, ties = c("breslow"))
Bipolar.dia.cox.rand.clustered
#95%CI for HR
exp(confint(Bipolar.dia.cox.rand.clustered))
```

## Sensitivity check

### Mixed-effect Cox model without estimated stratified hazard by study

Recommended sensitivity check model from Keele Univerisity IPD-MA workshop

```{r}
dia.cox.rand.shared <-
  coxme(
    dia.object ~ baseMem + (1 + baseMem |
                              Study) ,
    data = dz,
    ties = c("breslow")
  )
dia.cox.rand.shared
```

```{r}
dep.dia.cox.rand.shared <-
  coxme(
    dep_dia_object ~ baseMem + (1 + baseMem |
                                  Study) ,
    data = dz,
    ties = c("breslow")
  )
dep.dia.cox.rand.shared
```

```{r}
eat.dia.cox.rand.shared <-
  coxme(
    eat_dia_object ~ baseMem + (1 + baseMem |
                                  Study) ,
    data = dz,
    ties = c("breslow")
  )
eat.dia.cox.rand.shared
```

```{r}
anx.dia.cox.rand.shared <-
  coxme(
    anx_dia_object ~ baseMem + (1 + baseMem |
                                  Study),
    data = dz,
    ties = c("breslow")
  )
anx.dia.cox.rand.shared
```

```{r}
Stress.dia.cox.rand.shared <-
  coxme(
    Stress_dia_object ~ baseMem + (1 + baseMem |
                                     Study),
    data = dz,
    ties = c("breslow")
  )
Stress.dia.cox.rand.shared
```

```{r}
Bipolar.dia.cox.rand.shared <-
  coxme(
    Bipolar_dia_object ~ baseMem + (1 + baseMem |
                                      Study.f),
    data = dz,
    ties = c("breslow")
  )
Bipolar.dia.cox.rand.shared
```

### IQ, age, sex covariates (where available)

```{r}
dia.cov.cox.rand.clustered <-
  coxme(
    dia.object ~ baseMem + (baseMem |
                              Study.n) + Study + Baseline_IQ + Age + Sex,
    data = dz,
    ties = c("breslow")
  )
dia.cov.cox.rand.clustered
```

```{r}
dep.cov.cox.rand.clustered <-
  coxme(
    dep_dia_object ~ baseMem + (baseMem |
                              Study.n) + Study + Baseline_IQ + Age + Sex,
    data = dz,
    ties = c("breslow")
  )
dep.cov.cox.rand.clustered
```

```{r}
eat.cov.cox.strata <-
  coxph(
    eat_dia_object ~ strata(Study.f) + baseMem + Age + Sex,
    data = dz,
    ties = c("breslow")
  )
eat.cov.cox.strata
```

## Moderator analysis

```{r prepare dataset}
d <- d%>% group_by(Study) %>%
  mutate(nameDepSx = ifelse(Study == "Nixon_PTSD", "CDI_t", NA),
         nameDepSx = ifelse(Study == "Woody", "CDI", nameDepSx)) %>%
  ungroup()
```

CDI cutoff - Timbremont et al., 2004

CDI t-score cutoff - +1SD above mean; e.g., Stazyk et al., 2017, Marwitz & Pringsheim, 2018

sMFQ cutoff - Eyre et al., 2021

MFQ cutoff - Daviss et al., 2006

RCA cutoff - Chorpita et al., 2005

```{r mutating relevant variables}
d <-
  d %>% mutate(
    nameDepSx = ifelse(
      Study %in% c(
        "Askelund",
        "Gutenbrunner",
        "Hamlat",
        "Hiller",
        "Hitchcock",
        "Hitchcock2",
        "Nixon_ASD",
        "Rice"
      ),
      Self_dep,
      nameDepSx
    ),
    nameDepSx = ifelse(Study == "Warne", "sMFQ", nameDepSx)
  )

dep.scale.cut.off = c(
  CDI = 16,
  CDI_t = 65,
  sMFQ = 12,
  MFQ = 29,
  RCA = 11
)

d <-
  d %>% mutate(Baseline_dep_sx_cutoff = ifelse(baseDepSx >= dep.scale.cut.off[nameDepSx], 1, 0))

dz$Baseline_dep_dia_sx <- d$Baseline_dep_sx_cutoff
```

### Age as a moderator of mem spec and dep sx

```{r}
dz <- dz %>% group_by(Study) %>% 
  mutate(Age.mean = mean(Age, na.rm = T),
         Age.cen = Age - Age.mean) %>% 
  ungroup()

#within study interaction term of base mem and Age
dz$ws.age.int <- dz$baseMem*dz$Age.cen

#across study interaction of base mem and Age
dz$acr.age.int <- dz$baseMem*dz$Age.mean
```

```{r dep sx at multiple time points with mem:Age interaction}
depSxmodel.Age.int   <-
  lme(
    depSx ~ baseMem + baseDepSx + ws.age.int + acr.age.int + Age.mean + Age.cen + timeDep,
    data = dz,
    random    = ~ 1 + acr.age.int + ws.age.int |
      Study ,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )

summary(depSxmodel.Age.int)
```

### Sex as a moderator of mem spec and dep sx

```{r}
dz$Sex <- as.numeric(dz$Gender)

dz <- dz %>% group_by(Study) %>% 
  mutate(Sex.mean = mean(Sex, na.rm = T),
         Sex.cen = Sex - Sex.mean) %>% 
  ungroup()

dz$ws.sex.int <- dz$baseMem*dz$Sex.cen
dz$acr.sex.int <- dz$baseMem*dz$Sex.mean
```

```{r dep sx at multiple time points with mem:sex interaction}
depSxmodel.sex.int   <-
  lme(
    depSx ~ baseMem + baseDepSx +  ws.sex.int + acr.sex.int + Sex.cen + Sex.mean + timeDep,
    data = dz,
    random    = ~ 1 + acr.sex.int + ws.sex.int |
      Study ,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )

summary(depSxmodel.sex.int)
```

### Trauma history as a moderator

```{r mean centering}
dz <- dz %>% group_by(Study) %>% 
  mutate(Trauma.mean = mean(Trauma_exposed, na.rm = T),
         Trauma.cen = Trauma_exposed - Trauma.mean) %>% 
  ungroup()

dz$ws.trauma.int <- dz$baseMem* dz$Trauma.cen
dz$acr.trauma.int <- dz$baseMem* dz$Trauma.mean
```

```{r dep sx at multiple time points with mem:trauma interaction}
depSxmodel.trauma.int   <-
  lme(
    depSx ~ baseMem + baseDepSx + ws.trauma.int + acr.trauma.int + Trauma.mean + Trauma.cen + timeDep,
    data = dz,
    random    = ~ 1 + acr.trauma.int + ws.trauma.int |
      Study ,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )

summary(depSxmodel.trauma.int)
```

### Family history as a moderator

```{r mean centering}
dz <- dz %>% group_by(Study) %>% 
  mutate(famHis.mean = mean(Family_mental_illness, na.rm = T),
         famHis.cen = Family_mental_illness - famHis.mean) %>% 
  ungroup()

dz$ws.famHis.int <- dz$baseMem* dz$famHis.cen
dz$acr.famHis.int <- dz$baseMem* dz$famHis.mean
```

```{r dep sx at multiple time points with mem:family history interaction}
depSxmodel.famHis.int   <-
  lme(
    depSx ~ baseMem + baseDepSx + ws.famHis.int + acr.famHis.int + famHis.mean + famHis.cen +
      timeDep,
    data = dz,
    random    = ~ 1 + acr.famHis.int + ws.famHis.int |
      Study ,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )

summary(depSxmodel.famHis.int)
```

### Baseline depression as a moderator

```{r}
dz <- dz %>% group_by(Study) %>% 
  mutate(Dep.mean = mean(Baseline_dep_dia_sx, na.rm = T),
         Dep.cen = Baseline_dep_dia_sx - Dep.mean) %>% 
  ungroup()

dz$ws.dep.int <- dz$baseMem*dz$Dep.cen
dz$acr.dep.int <- dz$baseMem*dz$Dep.mean
```

```{r dep sx at multiple time points with mem:baseDep interaction}
depSxmodel.dep.int   <-
  lme(
    depSx ~ baseMem + ws.dep.int + acr.dep.int + Dep.cen + Dep.mean + timeDep,
    data = dz,
    random    = ~ 1 + acr.dep.int + ws.dep.int |
      Study ,
    na.action = na.omit,
    control   = lmeControl(opt = 'optim')
  )

summary(depSxmodel.dep.int)
```

## Additional checks

### Multivariate model of depressive symptoms without participants that meets clinical cut-off at baseline

```{r, warning=F}
#Askelund 
#depression sx 6m
Ask.d6.sup1 <- single_ipd(dz%>% filter(Study == "Askelund" & Baseline_dep_dia_sx != 1), formula = "depSx6m ~baseMem + baseDepSx")
#depression sx 12m
Ask.d12.sup1 <- single_ipd(dz%>% filter(Study == "Askelund" & Baseline_dep_dia_sx != 1))

A_dm_fitsur_sup1 <- systemfit(list(dep6m = A_dm1, dep12m = A_dm2), data = subset(dz, Study =="Askelund" & Baseline_dep_dia_sx != 1),
                    method = "SUR")

Ask_dm_V11_sup1 <- A_dm_fitsur_sup1$coefCov["dep6m_baseMem", "dep6m_baseMem"]
Ask_dm_V12_sup1 <- A_dm_fitsur_sup1$coefCov["dep6m_baseMem", "dep12m_baseMem"]
Ask_dm_V22_sup1 <- A_dm_fitsur_sup1$coefCov["dep12m_baseMem", "dep12m_baseMem"]

#Rice
#depression sx 12m
Rice.d12.sup1 <- single_ipd(dz %>% filter(Study == "Rice" & Baseline_dep_dia_sx != 1))

Rice_dm_V22_sup1 <- Rice.d12.sup1$SE**2
```

```{r}
dep.mv.sup1 <- data.frame (
  Study = c("Askelund et al. 2019", "Gutenbrunner et al. 2018", "Hamlat et al. 2015", "Hiller unpub.", "Hipwell et al. 2011", "Hitchcock et al. 2014", "Hitchcock unpub.", "McCrory et al. 2017", "Nixon et al 2013a", "Nixon et al 2013b", "Rawal & Rice 2012", "Warne et al. 2020", "Woody et al. 2022"),
  n = c(930, 269, 397, 28, 236, 74, 195, 41, 65, 67, 259, 5880, 249),
  dep6m = c(Ask.d6.sup1$coef, 0.0000, Ham.d6$coef, Hil.d6$coef, 0.0000, Hit.d6$coef, 0.0000, 0.0000, NixA.d6$coef, NixP.d6$coef, 0.0000, 0.0000,  Wood.d6$coef),
  dep12m = c(Ask.d12.sup1$coef, Gut.d12$coef, Ham.d12$coef, 0.0000, Hip.d12$coef, 0.0000, Hit2.d12$coef, 0.0000, 0.0000, 0.0000, Rice.d12.sup1$coef, 0.0000, Wood.d12$coef),
  dep18m = c(0.0000, 0.0000, Ham.d18$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d18$coef),
  dep24m = c(0.0000, Gut.d24$coef, Ham.d24$coef, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood.d24$coef),
  dep48m = c(0.0000, 0.0000, Ham.d48$coef, 0.0000, 0.0000, 0.0000, 0.0000, Mc.d48$coef, 0.0000, 0.0000, 0.0000, Warn.d48$coef, 0.0000),
  V11 = c(Ask_dm_V11_sup1, 100000, Ham_dm_V11, Hil_dm_V11, 100000, Hit_dm_V11, 100000, 100000, NixA_dm_V11, NixP_dm_V11, 100000, 100000, Wood_dm_V11),
  V12 = c(Ask_dm_V12_sup1, 0.0000, Ham_dm_V12, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V12),
  V13 = c(0.0000, 0.0000, Ham_dm_V13, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V13),
  V14 = c(0.0000, 0.0000, Ham_dm_V14, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V14),
  V15 = c(0.0000, 0.0000, Ham_dm_V15, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V22 = c(Ask_dm_V22_sup1, Gut_dm_V22, Ham_dm_V22, 100000, Hip_dm_V22, 100000, Hit2_dm_V22, 100000, 100000, 100000, Rice_dm_V22_sup1, 100000, Wood_dm_V22),
  V23 = c(0.0000, 0.0000, Ham_dm_V23, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V23),
  V24 = c(0.0000, Gut_dm_V24, Ham_dm_V24, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V24),
  V25 = c(0.0000, 0.0000, Ham_dm_V25, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V33 = c(100000, 100000, Ham_dm_V33, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dm_V33),
  V34 = c(0.0000, 0.0000, Ham_dm_V34, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Wood_dm_V34),
  V35 = c(0.0000, 0.0000, Ham_dm_V35, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V44 = c(100000, Gut_dm_V44, Ham_dm_V44, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Wood_dm_V44),
  V45 = c(0.0000, 0.0000, Ham_dm_V45, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V55 = c(100000, 100000, Ham_dm_V55, 100000, 100000, 100000, 100000, Mc_dm_V55, 100000, 100000, 100000, Warn_dm_V55, 100000))
```

```{r}
y.sup1 <- as.matrix(dep.mv.sup1[3:7])
S.sup1 <- as.matrix(dep.mv.sup1[8:22])
model.dep.mv.sup1.1 <- mvmeta(y.sup1, S.sup1)
summary(model.dep.mv.sup1.1)
```

### Multivariate model with all psychopathology symptoms at earliest timepoint per study

```{r, warning=F}
#stage one
##Warne psychosis sx
Warn.psy48 <-
  single_ipd(dz %>% filter(Study == "Warne"), formula = "psySx48m ~ baseMem + basePsySx")

#obtaining covariance between outcomes per study
##Askelund
Ask_all_V11 <- Ask.d12$SE**2

#Gutenbrunner
G_all1 <- depSx ~ baseMem + baseDepSx 
G_all2 <- anxSx12m ~ baseMem + baseAnxSx 

G_all_fitsur <-
  systemfit(
    list(dep = G_all1, anx = G_all2),
    data = subset(dz, Study == "Gutenbrunner"),
    method = "SUR"
  )

Gut_all_V11 <- G_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Gut_all_V12 <- G_all_fitsur$coefCov["dep_baseMem", "anx_baseMem"]
Gut_all_V22 <- G_all_fitsur$coefCov["anx_baseMem", "anx_baseMem"]

#Hamlat
Ham_all1 <- depSx ~ baseMem + baseDepSx 
Ham_all2 <- anxSx6m ~ baseMem + baseAnxSx 

Ham_all_fitsur <-
  systemfit(
    list(dep = Ham_all1, anx = Ham_all2),
    data = subset(dz, Study == "Hamlat"),
    method = "SUR"
  )

Ham_all_V11 <- Ham_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Ham_all_V12 <- Ham_all_fitsur$coefCov["dep_baseMem", "anx_baseMem"]
Ham_all_V22 <- Ham_all_fitsur$coefCov["anx_baseMem", "anx_baseMem"]

#Hitchcock
Hit.d2 <-
  single_ipd(dz %>% filter(Study == "Hitchcock"), formula = "depSx ~baseMem + baseDepSx")

Hit_all1 <- depSx ~ baseMem + baseDepSx
Hit_all3 <- PTSDsx2m ~ baseMem + basePTSDsx 

Hit_all_fitsur <-
  systemfit(
    list(dep = Hit_all1, ptsd = Hit_all3),
    data = subset(dz, Study == "Hitchcock"),
    method = "SUR"
  )

Hit_all_V11 <- Hit_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Hit_all_V13 <- Hit_all_fitsur$coefCov["dep_baseMem", "ptsd_baseMem"]
Hit_all_V33 <- Hit_all_fitsur$coefCov["ptsd_baseMem", "ptsd_baseMem"]

#Hitchcock2
Hit2_all1 <- depSx ~ baseMem + baseDepSx 
Hit2_all2 <- anxSx12m ~ baseMem + baseAnxSx
Hit2_all3 <- PTSDsx8m ~ baseMem + basePTSDsx

Hit2_all_fitsur <-
  systemfit(
    list(dep = Hit2_all1, anx = Hit2_all2, ptsd = Hit2_all3),
    data = subset(dz, Study == "Hitchcock2"),
    method = "SUR"
  )

Hit2_all_V11 <- Hit2_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Hit2_all_V12 <- Hit2_all_fitsur$coefCov["dep_baseMem", "anx_baseMem"]
Hit2_all_V13 <- Hit2_all_fitsur$coefCov["dep_baseMem", "ptsd_baseMem"]
Hit2_all_V22 <- Hit2_all_fitsur$coefCov["anx_baseMem", "anx_baseMem"]
Hit2_all_V23 <- Hit2_all_fitsur$coefCov["anx_baseMem", "ptsd_baseMem"]
Hit2_all_V33 <- Hit2_all_fitsur$coefCov["ptsd_baseMem", "ptsd_baseMem"]

#Hiller 
Hil_all_V11 <- Hil.d6$SE**2

#Hipwell
Hip_all_V11 <- Hip.d12$SE**2

#McCrory
Mc_all1 <- depSx ~ baseMem + baseDepSx
Mc_all2 <- anxSx27m ~ baseMem + baseAnxSx

Mc_all_fitsur <-
  systemfit(
    list(dep = Mc_all1, anx = Mc_all2),
    data = subset(dz, Study == "McCrory"),
    method = "SUR"
  )

Mc_all_V11 <- Mc_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Mc_all_V12 <- Mc_all_fitsur$coefCov["dep_baseMem", "anx_baseMem"]
Mc_all_V22 <- Mc_all_fitsur$coefCov["anx_baseMem", "anx_baseMem"]

#NixonA
NixA_all1 <- depSx ~ baseMem + baseDepSx
NixA_all3 <- PTSDsx2m ~ baseMem + basePTSDsx

NixA_all_fitsur <-
  systemfit(
    list(dep = NixA_all1, ptsd = NixA_all3),
    data = subset(dz, Study == "Nixon_ASD"),
    method = "SUR"
  )

NixA_all_V11 <- NixA_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
NixA_all_V13 <- NixA_all_fitsur$coefCov["dep_baseMem", "ptsd_baseMem"]
NixA_all_V33 <- NixA_all_fitsur$coefCov["ptsd_baseMem", "ptsd_baseMem"]

#NixonP
NixP_all1 <- depSx ~ baseMem + baseDepSx
NixP_all3 <- PTSDsx2m ~ baseMem + basePTSDsx

NixP_all_fitsur <-
  systemfit(
    list(dep = NixP_all1, ptsd = NixP_all3),
    data = subset(dz, Study == "Nixon_PTSD"),
    method = "SUR"
  )

NixP_all_V11 <- NixP_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
NixP_all_V13 <- NixP_all_fitsur$coefCov["dep_baseMem", "ptsd_baseMem"]
NixP_all_V33 <- NixP_all_fitsur$coefCov["ptsd_baseMem", "ptsd_baseMem"]

#Rice
Rice_all_V11 <- Rice.d12$SE**2

#Warne
Wa_all1 <- depSx ~ baseMem + baseDepSx
Wa_all4 <- psySx48m ~ baseMem + basePsySx

Wa_all_fitsur <-
  systemfit(
    list(dep = Wa_all1, psychosis = Wa_all4),
    data = subset(dz, Study == "Warne"),
    method = "SUR"
  )

Warn_all_V11 <- Wa_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Warn_all_V14 <- Wa_all_fitsur$coefCov["dep_baseMem", "psychosis_baseMem"]
Warn_all_V44 <- Wa_all_fitsur$coefCov["psychosis_baseMem", "psychosis_baseMem"]

#Woody
Wo_all1 <- depSx ~ baseMem + baseDepSx
Wo_all2 <- anxSx6m ~ baseMem + baseAnxSx 

Wo_all_fitsur <-
  systemfit(
    list(dep = Wo_all1, anx = Wo_all2),
    data = subset(dz, Study == "Woody"),
    method = "SUR"
  )

Wood_all_V11 <- Wo_all_fitsur$coefCov["dep_baseMem", "dep_baseMem"]
Wood_all_V12 <- Wo_all_fitsur$coefCov["dep_baseMem", "anx_baseMem"]
Wood_all_V22 <- Wo_all_fitsur$coefCov["anx_baseMem", "anx_baseMem"]
```

```{r}
all.mv.sup2 <- data.frame (
  Study = c("Askelund et al. 2019", "Gutenbrunner et al. 2018", "Hamlat et al. 2015", "Hiller unpub.", "Hipwell et al. 2011", "Hitchcock et al. 2014", "Hitchcock unpub.", "McCrory et al. 2017", "Nixon et al 2013a", "Nixon et al 2013b", "Rawal & Rice 2012", "Warne et al. 2020", "Woody et al. 2022"),
  timeToFollowup = c(2, 12, 6, 6, 12, 2, 8, 27, 2, 2, 12, 48, 6),
  dep = c(Ask.d6$coef, Gut.d12$coef, Ham.d6$coef, Hil.d6$coef, Hip.d12$coef, Hit.d2$coef, Hit2.d12$coef, Mc.d48$coef, NixA.d6$coef, NixP.d6$coef, Rice.d12$coef, Warn.d48$coef,  Wood.d6$coef),
  anx = c(0.0000, Gut.a12$coef, Ham.a6$coef, 0.0000, 0.0000, 0.0000, Hit2.a12$coef, Mc.a27$coef, 0.0000, 0.0000, 0.0000, 0.0000, Wood.a6$coef), 
  ptsd = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Hit.p2$coef, Hit2.p8$coef, 0.0000, NixA.p2$coef, NixP.p2$coef, 0.0000, 0.0000, 0.0000),
  psychosis = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Warn.psy48$coef, 0.0000),
  V11 = c(Ask_all_V11, Gut_all_V11, Ham_all_V11, Hil_all_V11, Hip_all_V11, Hit_all_V11, Hit2_all_V11, Mc_all_V11, NixA_all_V11, NixP_all_V11, Rice_all_V11, Warn_all_V11, Wood_all_V11),
  V12 = c(0.0000, Gut_all_V12, Ham_all_V12, 0.0000, 0.0000, 0.0000, Hit2_all_V12, Mc_all_V12, 0.0000, 0.0000, 0.0000, 0.0000, Wood_all_V12),
  V13 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Hit_all_V13, Hit2_all_V13, 0.0000, NixA_all_V13, NixP_all_V13, 0.0000, 0.0000, 0.0000),
  V14 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Warn_all_V14),
  V22 = c(100000, Gut_all_V22, Ham_all_V22, 100000, 100000, 100000, Hit2_all_V22, Mc_all_V22, 100000, 100000, 100000, 100000, Wood_all_V22),
  V23 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, Hit2_all_V23, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V24 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V33 = c(100000, 100000, 100000, 100000, 100000, Hit_all_V33, Hit2_all_V33, 100000, NixA_all_V33, NixP_all_V33, 100000, 100000, 100000),
  V34 = c(0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000, 0.0000),
  V44 = c(100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, 100000, Warn_all_V44, 100000))
```

```{r}
y.all <- as.matrix(all.mv.sup2[3:6])
S.all <- as.matrix(all.mv.sup2[7:16])
all.mv.sup2.1 <- mvmeta(y.all, S.all)
summary(all.mv.sup2.1)
```

```{r}
all_mv_yi <- all.mv.sup2 %>% pivot_longer(cols = dep:psychosis, values_to = "Yi", names_to = "Symptom")
all_mv_V1i <- all.mv.sup2 %>% pivot_longer(cols = V11:V14, values_to = "V1i")
all_mv_V2i <- all.mv.sup2 %>% pivot_longer(cols = c(V12, V22:V24), values_to = "V2i")
all_mv_V3i <- all.mv.sup2 %>% pivot_longer(cols = c(V13, V23, V33, V34), values_to = "V3i")
all_mv_V4i <- all.mv.sup2 %>% pivot_longer(cols = c(V14, V24, V34, V44), values_to = "V4i")

all_mv_l <- cbind(all_mv_yi %>% select(Study, Symptom, Yi), all_mv_V1i %>% select(V1i), all_mv_V2i %>% select(V2i), all_mv_V3i%>% select(V3i), all_mv_V4i %>% select(V4i))
```

```{r, warning=F}
#construct full (block-diagonal) variance covariance matrix for all studies
V.all <- bldiag(lapply(split(all_mv_l[,c("V1i", "V2i", "V3i","V4i")], all_mv_l$Study), as.matrix))

all.mv.sup2.2 <- rma.mv(Yi, V.all, mods = ~Symptom - 1, random = ~ Symptom|Study, 
              struct="UN", data=all_mv_l, method="REML")
print(all.mv.sup2.2, digits=3)
```

### Use clinical cut-off on depressive sx to apply Cox models

```{r, warning=F}
# look for columns that have _self_dep (for self-report of dep sx)
dep.sx.columns = grep("_self_dep", colnames(d), value = T)
# check if column starts with Base to set time=0, otherwise extract time in months from end of column name
dep.sx.columns.time = ifelse(grepl("^Base", dep.sx.columns), 0, as.numeric(gsub(
  ".*_dep_", "", gsub("m$", "", dep.sx.columns)
)))

d = as.data.frame(d)
d$above.cutoff.time = NA
d$above.cutoff = NA

for(i in 1:length(dep.sx.columns)){
  column = dep.sx.columns[i]
  time = dep.sx.columns.time[i]
  above.cutoff.rows = which(d[,column] >= dep.scale.cut.off[d$nameDepSx]) 
  below.cutoff.rows = which(d[,column] < dep.scale.cut.off[d$nameDepSx])
  still.below.cutoff.rows = intersect(below.cutoff.rows, which(d[,'above.cutoff']==0))
  newly.below.cutoff.rows = intersect(below.cutoff.rows, which(is.na(d[,'above.cutoff'])))
  already.above.cutoff.rows = intersect(above.cutoff.rows, which(d[,'above.cutoff']==1))
  newly.above.cutoff.rows = setdiff(above.cutoff.rows, which(d[,'above.cutoff']==1))
  
  d[above.cutoff.rows,'above.cutoff'] = 1
  d[below.cutoff.rows,'above.cutoff'] = ifelse(is.na(d[below.cutoff.rows,'above.cutoff']), 0,
                                          pmax(d[below.cutoff.rows,'above.cutoff'],0)) 
  # pmax (parallel maximum) sets to 0 if already 0 and 1 if already diagnosed
  
  
  if(length(already.above.cutoff.rows)>0){
     d[already.above.cutoff.rows,'above.cutoff.time'] = pmin(d[already.above.cutoff.rows,'above.cutoff.time'], time,na.rm=T)
  }
  if(length(newly.above.cutoff.rows)>0){
    d[newly.above.cutoff.rows,'above.cutoff.time'] = time
  }
 
  if(length(still.below.cutoff.rows)>0){
    d[still.below.cutoff.rows,'above.cutoff.time'] = pmax(d[still.below.cutoff.rows,'above.cutoff.time'], time,na.rm=T)
  }
  if(length(newly.below.cutoff.rows)>0){
    d[newly.below.cutoff.rows,'above.cutoff.time'] = time
  }
  
}

#manually check
#d[,c("nameDepSx", "above.cutoff", "above.cutoff.time", dep.sx.columns[order(dep.sx.columns.time)])] %>% View()
```

```{r}
dep.sx.object <- Surv(d$above.cutoff.time, d$above.cutoff)

dep.sx.cox.rand.clustered <- coxme(
  dep.sx.object ~ baseMem + (baseMem |
                               Study) + Study,
  data = dz,
  ties = c("breslow")
)

dep.sx.cox.rand.clustered
exp(confint(dep.sx.cox.rand.clustered))
```

Is there more discrepancy between clinician-rated and self-report in people with low memory specificity compared to people with high memory specificity?

#### At baseline

```{r}
dz = dz %>% mutate(
  Baseline_dep_dia_int = case_when(
    is.na(Depressive_disorders_time) ~ NA,
    Depressive_disorders_diagnosed == 1 &
      Depressive_disorders_time == 0 ~ 1,
    .default = 0
  )
)
```

```{r,warning=F}
p = dz %>%
  group_by(memCat) %>%
  mutate(weight = 1 / sum(!is.na(Baseline_dep_dia_int) &
                            !is.na(Baseline_dep_dia_sx))) %>%
  ggplot(aes(abs(
    Baseline_dep_dia_int - Baseline_dep_dia_sx
  ))) +
  facet_wrap( ~ memCat) +
  geom_histogram(
    aes(weight = weight),
    bins = 2,
    binwidth = 0.3,
    alpha = 0.7
  ) +
  xlab("Self-report and Clinician-rated Discrepancy") +
  ylab("Proportion") +
  theme_bw()
print(p)
```

```{r}
diff.table.baseline = table(dz$memCat,
                            abs(dz$Baseline_dep_dia_int - dz$Baseline_dep_dia_sx))

fisher.test(diff.table.baseline)
```

#### At 12m follow-up

```{r, warning=F}
d = d %>% 
  mutate(Dep_dia_sx_12m = ifelse(Followup_self_dep_12m >= dep.scale.cut.off[nameDepSx], 1, 0))

dz$Dep_dia_sx_12m = d$Dep_dia_sx_12m

p.12m = dz %>%
  group_by(memCat) %>%
  mutate(weight = 1 / sum(!is.na(Dep_dia_sx_12m) &
                            !is.na(Followup_int_dep_dia_12m))) %>%
  ggplot(aes(abs(
    Dep_dia_sx_12m - Followup_int_dep_dia_12m
  ))) +
  facet_wrap( ~ memCat) +
  geom_histogram(
    aes(weight = weight),
    bins = 2,
    binwidth = 0.3,
    alpha = 0.7
  ) +
  xlab("Self-report and Clinician-rated Discrepancy") +
  ylab("Proportion") +
  theme_bw()

print(p.12m)

diff.table.12m = table(dz$memCat,
                             abs(dz$Dep_dia_sx_12m - dz$Followup_int_dep_dia_12m))

fisher.test(diff.table.12m)
```

# References

Chorpita, B. F., Moffitt, C. E., & Gray, J. (2005). Psychometric properties of the Revised Child Anxiety and Depression Scale in a clinical sample. *Behaviour research and therapy*, *43*(3), 309-322.

Daviss, W. B., Birmaher, B., Melhem, N. A., Axelson, D. A., Michaels, S. M., & Brent, D. A. (2006). Criterion validity of the Mood and Feelings Questionnaire for depressive episodes in clinic and non‐clinic subjects. *Journal of Child Psychology and Psychiatry*, *47*(9), 927-934.

Eyre, O., Jones, R. B., Agha, S. S., Wootton, R. E., Thapar, A. K., Stergiakouli, E., Langley, K., Collishaw, S., Thapar, A., & Riglin, L. (2021). Validation of the short Mood and Feelings Questionnaire in young adulthood. *Journal of Affective Disorders*, *294*, 883-888.

Marwitz, L., & Pringsheim, T. (2018). Clinical utility of screening for anxiety and depression in children with Tourette syndrome. *Journal of the Canadian Academy of Child and Adolescent Psychiatry*, *27*(1), 15.

Riley, R. D., Tierney, J. F., & Stewart, L. A. (2021). *Individual participant data meta-analysis: a handbook for healthcare research*. John Wiley & Sons.

Stazyk, K., DeMatteo, C., Moll, S., & Missiuna, C. (2017). Depression in youth recovering from concussion: correlates and predictors. *Brain injury*, *31*(5), 631-638.

Timbremont, B., Braet, C., & Dreessen, L. (2004). Assessing depression in youth: relation between the Children's Depression Inventory and a structured interview. *Journal of Clinical Child and Adolescent Psychology*, *33*(1), 149-157.
